---
title: "Test paper - sentiments"
author: "Giulia Grisot"
date: "2020"
output:
  html_notebook: 
    theme: flatly
    fig_width: 10
    fig_height: 7
---

# Corpus preparation

```{r message=FALSE, warning=F}
library(tidyverse)
# library(harrypotter)
library(lme4)
library(tidytext)
library(sjPlot)
library(ggplot2)
library(ggsci)
library(ggpubr)

```

# make corpus by word 

```{r}
 corpus_all_entities_long <- corpus_all_entities %>%
  unnest_tokens(word, text, to_lower = F) %>%
  group_by(doc_id) %>%
  dplyr::mutate(word_id = row_number()) %>%
  group_by(word) %>%
  dplyr::mutate(freqency = n()) %>%
  ungroup()
# %>%
#   mutate(type = ifelse(type == "CH_urban", "urban", "rural"))
# mutate(urban_rural = ifelse(type == "CH_city_village" | type == "CH_building_spots" | type == "CH_country_regions" | type == "CH_roads", "urban", "rural"))

```

since natural terms are part of the rural sphere, let's unify nat term and rural labels:
```{r}
corpus_all_entities_long$type[corpus_all_entities_long$type == "nat_terms"] <- "CH_rural"

```


```{r}
theme_set(theme_light()) # set default ggplot theme to light
fs = 10 # default plot font size
```

# Freq per book

```{r}
corpus_all_entities_long[,c("title","word")]  %>%
  group_by(title, word) %>%
  anti_join(stop_german, by = "word") %>% # delete stopwords
  count() %>% # summarize count per word per title
  arrange(desc(n)) %>% # highest freq on top
  group_by(title) %>% # 
  mutate(top = seq_along(word)) %>% # identify rank within group
  filter(top <= 15) %>% # retain top 15 frequent words
  # create barplot
  ggplot(aes(x = -top, fill = title)) + 
  geom_bar(aes(y = n), stat = 'identity', col = 'black') +
  # make sure words are printed either in or next to bar
  geom_text(aes(y = ifelse(n > max(n) / 2, max(n) / 50, n + max(n) / 50),
                label = word), size = fs/3, hjust = "left") +
  theme_sjplot2() +
  theme(legend.position = 'none', # get rid of legend
        text = element_text(size = fs), # determine fs
        axis.text.x = element_text(angle = 45, hjust = 1, size = fs/1.5), # rotate x text
        axis.ticks.y = element_blank(), # remove y ticks
        axis.text.y = element_blank()) + # remove y text
  labs(y = "Word count", x = "", # add labels
       title = "Most frequent words by book") +
  facet_grid(. ~ title) + # separate plot for each book
  coord_flip() + # flip axes
  # scale_fill_hp(discrete = T, option = "Always")
  scale_fill_simpsons()

```

# Freq per entity type

```{r}

corpus_all_entities_long[,c("type","word")]  %>%
  group_by(type, word) %>%
  anti_join(stop_german, by = "word") %>% # delete stopwords
  count() %>% # summarize count per word per title
  arrange(desc(n)) %>% # highest freq on top
  group_by(type) %>% # 
  mutate(top = seq_along(word)) %>% # identify rank within group
  filter(top <= 15) %>% # retain top 15 frequent words
  # create barplot
  ggplot(aes(x = -top, fill = type)) + 
  geom_bar(aes(y = n), stat = 'identity', col = 'black') +
  # make sure words are printed either in or next to bar
  geom_text(aes(y = ifelse(n > max(n) / 2, max(n) / 50, n + max(n) / 50),
                label = word), size = fs/3, hjust = "left") +
  theme_sjplot2() +
  theme(legend.position = 'none', # get rid of legend
        text = element_text(size = fs), # determine fs
        axis.text.x = element_text(angle = 45, hjust = 1, size = fs/1.5), # rotate x text
        axis.ticks.y = element_blank(), # remove y ticks
        axis.text.y = element_blank()) + # remove y text
  labs(y = "Word count", x = "", # add labels
       title = "Most frequent words by type") +
  facet_grid(. ~ type) + # separate plot for each book
  coord_flip() + # flip axes
  # scale_fill_hp(discrete = T, option = "Always")
  scale_fill_simpsons()

```

# Sentiments by type

## BAWL 

```{r}

corpus_BAWL <- corpus_all_entities_long %>%
  anti_join(stop_german, by = "word") %>%
  left_join(BAWL_emotions, by = "word")

```


### arousal

```{r}
corpus_BAWL %>%
  # summarise(value = mean(value)) %>%
  ggplot(aes(x = type, y = arousal, fill = type)) +
  # ylim(-2,2) +
  # facet_wrap(~ type, scales = "free_y") +
  geom_boxplot() +
  theme_sjplot2() +
  theme(legend.position = 'none', # get rid of legend
        axis.text.x = element_text(angle = 45, hjust = 1, size = fs/1.5)) + 
  scale_fill_simpsons() +
    ggpubr::stat_compare_means(method = "wilcox.test",
                             comparisons = list(c("CH_rural", "CH_urban")),
                             na.rm = T,
                             label = "p.signif")
```

```{r}

Rmisc::summarySE(corpus_BAWL, measurevar = "arousal",
          groupvars = c("type"),
          na.rm = TRUE,
          conf.interval = 0.95)

```

```{r}

compare_means(arousal ~ type, data = corpus_BAWL, method = "wilcox.test")


```

```{r}
BAWL_arousal_lmer <- lmer(arousal ~ type + log(freqency) +
                            (1|title),
                          corpus_BAWL, REML = F)

summary(BAWL_arousal_lmer)

```


### valence

```{r}
corpus_BAWL  %>%
  # summarise(value = mean(value)) %>%
  ggplot(aes(x = type, y = valence, fill = type)) +
  # ylim(-2,2) +
  # facet_wrap(~ type, scales = "free_y") +
  geom_boxplot() +
  theme_sjplot2() +
  theme(legend.position = 'none', # get rid of legend
        axis.text.x = element_text(angle = 45, hjust = 1, size = fs/1.5)) + 
  scale_fill_simpsons() +
    ggpubr::stat_compare_means(method = "wilcox.test",
                             comparisons = list(c("CH_rural", "CH_urban")),
                             na.rm = T,
                             label = "p.signif")
```

```{r}

Rmisc::summarySE(corpus_BAWL, measurevar = "valence",
          groupvars = c("type"),
          na.rm = TRUE,
          conf.interval = 0.95)

```

```{r}

compare_means(valence ~ type, data = corpus_BAWL, method = "wilcox.test")


```

```{r}
BAWL_valence_lmer <- lmer(valence ~ type + log(freqency) +
       (1|title),
     corpus_BAWL, REML = F)

summary(BAWL_valence_lmer)
```

### imageability

```{r}
corpus_BAWL  %>%
  # summarise(value = mean(value)) %>%
  ggplot(aes(x = type, y = imageability, fill = type)) +
  # ylim(-2,2) +
  # facet_wrap(~ type, scales = "free_y") +
  geom_boxplot() +
  theme_sjplot2() +
  theme(legend.position = 'none', # get rid of legend
        axis.text.x = element_text(angle = 45, hjust = 1, size = fs/1.5)) + 
  scale_fill_simpsons() +
    ggpubr::stat_compare_means(method = "wilcox.test",
                             comparisons = list(c("CH_rural", "CH_urban")),
                             na.rm = T,
                             label = "p.signif")
```

```{r}

Rmisc::summarySE(corpus_BAWL, measurevar = "imageability",
          groupvars = c("type"),
          na.rm = TRUE,
          conf.interval = 0.95)

```

```{r}

compare_means(imageability ~ type, data = corpus_BAWL, method = "wilcox.test")


```

```{r}
BAWL_imag_lmer <- lmer(imageability ~ type + log(freqency) +
       (1|title),
     corpus_BAWL, REML = F)

summary(BAWL_imag_lmer)
```

## SentiWS 

```{r}

corpus_sentiWS <- corpus_all_entities_long %>%
  anti_join(stop_german, by = "word") %>%
  left_join(sentiWS_long, by = "word")

```


### polarity

```{r}
corpus_sentiWS %>%
  # summarise(value = mean(value)) %>%
  ggplot(aes(x = type, y = SentiWS_polarity, fill = type)) +
  # ylim(-2,2) +
  # facet_wrap(~ type, scales = "free_y") +
  geom_boxplot() +
  theme_sjplot2() +
  theme(legend.position = 'none', # get rid of legend
        axis.text.x = element_text(angle = 45, hjust = 1, size = fs/1.5)) + 
  scale_fill_simpsons() +
    ggpubr::stat_compare_means(method = "wilcox.test",
                             comparisons = list(c("CH_rural", "CH_urban")),
                             na.rm = T,
                             label = "p.signif")
                             
    # ggpubr::stat_compare_means(method = "wilcox.test", 
                               # aes(group = type), 
                             # label = "p.signif", 
                             # label.x = 1.5, na.rm = TRUE)
```

```{r}

Rmisc::summarySE(corpus_sentiWS, measurevar = "SentiWS_polarity",
          groupvars = c("type"),
          na.rm = TRUE,
          conf.interval = 0.95)

```

```{r}

compare_means(SentiWS_polarity ~ type, data = corpus_sentiWS, method = "wilcox.test")


```

```{r}
SentiWS_polarity_lmer <- lmer(SentiWS_polarity ~ type + log(freqency) +
                            (1|title),
     corpus_sentiWS, REML = F)

summary(SentiWS_polarity_lmer)

```

## LANG 

```{r}

corpus_LANG <- corpus_all_entities_long %>%
  anti_join(stop_german, by = "word") %>%
 left_join(LANG_processed, by = "word")

# ks.test(corpus_LANG$arousal_mean, "pnorm", mean=mean(corpus_LANG$arousal_mean), sd=sd(corpus_LANG$arousal_mean))
# ks.test(corpus_LANG$valence_mean, "pnorm", mean=mean(corpus_LANG$valence_mean), sd=sd(corpus_LANG$valence_mean))
# 

# ggplot(corpus_LANG, aes(arousal_mean)) +
#   geom_histogram()
# ggplot(corpus_LANG, aes(valence_mean)) +
#   geom_histogram()

```


### arousal

```{r}
corpus_LANG %>%
  # summarise(value = mean(value)) %>%
  ggplot(aes(x = type, y = arousal_mean, fill = type)) +
  # ylim(-2,2) +
  # facet_wrap(~ type, scales = "free_y") +
  geom_boxplot() +
  theme_sjplot2() +
  theme(legend.position = 'none', # get rid of legend
        axis.text.x = element_text(angle = 45, hjust = 1, size = fs/1.5)) + 
  scale_fill_simpsons() +
    ggpubr::stat_compare_means(method = "wilcox.test",
                             comparisons = list(c("CH_rural", "CH_urban")),
                             na.rm = T,
                             label = "p.signif")
                             
    # ggpubr::stat_compare_means(method = "wilcox.test", 
                               # aes(group = type), 
                             # label = "p.signif", 
                             # label.x = 1.5, na.rm = TRUE)
```

```{r}

Rmisc::summarySE(corpus_LANG, measurevar = "arousal_mean",
          groupvars = c("type"),
          na.rm = TRUE,
          conf.interval = 0.95)

```

```{r}

compare_means(arousal_mean ~ type, data = corpus_LANG, method = "wilcox.test")


```

```{r}
LANG_arousal_lmer <- lmer(arousal_mean ~ type + log(freqency) +
                            (1|title),
     corpus_LANG, REML = F)

summary(LANG_arousal_lmer)

```

### valence

```{r}
corpus_LANG %>%
  # summarise(value = mean(value)) %>%
  ggplot(aes(x = type, y = valence_mean, fill = type)) +
  # ylim(-2,2) +
  # facet_wrap(~ type, scales = "free_y") +
  geom_boxplot() +
  theme_sjplot2() +
  theme(legend.position = 'none', # get rid of legend
        axis.text.x = element_text(angle = 45, hjust = 1, size = fs/1.5)) + 
  scale_fill_simpsons() +
    ggpubr::stat_compare_means(method = "wilcox.test",
                             comparisons = list(c("CH_rural", "CH_urban")),
                             na.rm = T,
                             label = "p.signif")
                             
    # ggpubr::stat_compare_means(method = "wilcox.test", 
                               # aes(group = type), 
                             # label = "p.signif", 
                             # label.x = 1.5, na.rm = TRUE)
```

```{r}

Rmisc::summarySE(corpus_LANG, measurevar = "valence_mean",
          groupvars = c("type"),
          na.rm = TRUE,
          conf.interval = 0.95)

```

```{r}

compare_means(valence_mean ~ type, data = corpus_LANG, method = "wilcox.test")


```

```{r}
LANG_arousal_lmer <- lmer(arousal_mean ~ type + log(freqency) +
                            (1|title),
     corpus_LANG, REML = F)

summary(LANG_arousal_lmer)

```

## Klinger

```{r}
corpus_klinger <- corpus_all_entities_long %>%
  anti_join(stop_german, by = "word") %>%
  left_join(klinger, by = "word")

```


### emotions

```{r}

corpus_klinger %>%
  group_by(title, emotion) %>%
  filter(!is.na(emotion)) %>%
  summarize(count = n()) %>%
  ggplot(aes(x = emotion, y = count, fill = emotion)) +    
  geom_bar(stat = 'identity') +
  theme_sjplot2() +
  theme(legend.position = 'none', # get rid of legend
        axis.text.x = element_text(angle = 45, hjust = 1, size = fs/1.5)) + 
  scale_fill_simpsons()

```

### Words carrying strongest emotions Plutchnik

```{r fig.height=7, fig.width=10}

corpus_klinger %>% 
  group_by(word, emotion) %>%
  count() %>% # summarize count per word per sentiment
  group_by(emotion) %>%
  arrange(emotion, desc(n)) %>% # most frequent on top
  mutate(top = seq_along(word)) %>% # identify rank within group
  filter(top <= 15) %>% # keep top 15 frequent words
  ggplot(aes(x = -top, fill = factor(emotion))) + 
  # create barplot
  geom_bar(aes(y = n), stat = 'identity', col = 'black') +
  # make sure words are printed either in or next to bar
  geom_text(aes(y = ifelse(n > max(n) / 2, max(n) / 50, n + max(n) / 50),
                label = word), size = fs/3, hjust = "left") +
  theme_sjplot2() +
  scale_fill_jco() +
  theme(legend.position = 'none', # remove legend
        text = element_text(size = fs), # determine fs
        axis.text.x = element_text(angle = 45, hjust = 1), # rotate x text
        axis.ticks.y = element_blank(), # remove y ticks
        axis.text.y = element_blank()) + # remove y text
  labs(y = "Word count", x = "", # add manual labels
       title = "Words carrying strongest emotions") +
  facet_grid(. ~ emotion, scales = "free") + # separate plot for each sentiment
  coord_flip() # flip axes


```


```{r}
summary(corpus_klinger)
```

```{r}
corpus_klinger %>%
  filter(!is.na(emotion)) %>%
  ggplot(aes(emotion, fill = type)) +
  geom_bar(stat = "count", position = "dodge", show.legend = T) +
  theme_sjplot2() +
  scale_fill_simpsons() +
  theme(legend.position = "bottom",
        text = element_text(size = fs), # determine fs
        axis.text.x = element_text(angle = 45, hjust = 1) # rotate x text
        )
```



```{r}

# corpus_plutchik <- corpus_plutchik %>%
#   group_by(type, emotion) %>%
#   mutate(emotion_proportion = n()) %>%
#   ungroup()
# 
# corpus_plutchik <- corpus_plutchik %>%
#   group_by(type) %>%
#   mutate(emotion_proportion2 = n()) %>%
#   ungroup()
# 
# corpus_plutchik <- corpus_plutchik %>%
#   mutate(emotion_proportion = emotion_proportion/emotion_proportion2*100)
# 
# corpus_plutchik$emotion_proportion2 <- NULL




ggplot(corpus_klinger, aes(emotion, fill = type)) +
  geom_bar(stat = "count", position = "fill") +
  theme_sjplot2() +
  scale_fill_simpsons() +
  theme(legend.position = "bottom",
        text = element_text(size = fs), # determine fs
        axis.text.x = element_text(angle = 45, hjust = 1) # rotate x text
        )


```


```{r}
corpus_klinger %>%
  filter(!is.na(emotion)) %>%
  ggplot(aes(emotion, fill = type)) +
  geom_histogram(stat = "count", position = "dodge") +
  facet_wrap(. ~ title, scales = "free_y")  +
  theme_sjplot2() +
  scale_fill_simpsons() +
  theme(legend.position = "bottom",
        text = element_text(size = fs), # determine fs
        axis.text.x = element_text(angle = 45, hjust = 1) # rotate x text
        )

```

## Plutchnik

```{r}
corpus_plutchik <- corpus_all_entities_long %>%
  anti_join(stop_german, by = "word") %>%
  left_join(plutchik, by = "word")

```


### emotions

```{r}

corpus_plutchik %>%
  
  group_by(title, emotion) %>%
  filter(!is.na(emotion)) %>%
  summarize(count = n()) %>%
  ggplot(aes(x = emotion, y = count, fill = emotion)) +    
  geom_bar(stat = 'identity') +
  theme_sjplot2() +
  theme(legend.position = 'none', # get rid of legend
        axis.text.x = element_text(angle = 45, hjust = 1, size = fs/1.5)) + 
  scale_fill_simpsons()

```

### Words carrying strongest emotions Plutchnik

```{r fig.height=7, fig.width=10}

corpus_plutchik %>% 
  group_by(word, emotion) %>%
  count() %>% # summarize count per word per sentiment
  group_by(emotion) %>%
  arrange(emotion, desc(n)) %>% # most frequent on top
  mutate(top = seq_along(word)) %>% # identify rank within group
  filter(top <= 15) %>% # keep top 15 frequent words
  ggplot(aes(x = -top, fill = factor(emotion))) + 
  # create barplot
  geom_bar(aes(y = n), stat = 'identity', col = 'black') +
  # make sure words are printed either in or next to bar
  geom_text(aes(y = ifelse(n > max(n) / 2, max(n) / 50, n + max(n) / 50),
                label = word), size = fs/3, hjust = "left") +
  theme_sjplot2() +
  scale_fill_jco() +
  theme(legend.position = 'none', # remove legend
        text = element_text(size = fs), # determine fs
        axis.text.x = element_text(angle = 45, hjust = 1), # rotate x text
        axis.ticks.y = element_blank(), # remove y ticks
        axis.text.y = element_blank()) + # remove y text
  labs(y = "Word count", x = "", # add manual labels
       title = "Words carrying strongest emotions") +
  facet_grid(. ~ emotion, scales = "free") + # separate plot for each sentiment
  coord_flip() # flip axes


```


```{r}
summary(corpus_plutchik)
```

```{r}
corpus_plutchik %>%
  filter(!is.na(emotion)) %>%
  ggplot(aes(emotion, fill = type)) +
  geom_bar(stat = "count", position = "dodge", show.legend = T) +
  theme_sjplot2() +
  scale_fill_simpsons() +
  theme(legend.position = "bottom",
        text = element_text(size = fs), # determine fs
        axis.text.x = element_text(angle = 45, hjust = 1) # rotate x text
        )
```



```{r}

# corpus_plutchik <- corpus_plutchik %>%
#   group_by(type, emotion) %>%
#   mutate(emotion_proportion = n()) %>%
#   ungroup()
# 
# corpus_plutchik <- corpus_plutchik %>%
#   group_by(type) %>%
#   mutate(emotion_proportion2 = n()) %>%
#   ungroup()
# 
# corpus_plutchik <- corpus_plutchik %>%
#   mutate(emotion_proportion = emotion_proportion/emotion_proportion2*100)
# 
# corpus_plutchik$emotion_proportion2 <- NULL




ggplot(corpus_plutchik, aes(emotion, fill = type)) +
  geom_bar(stat = "count", position = "fill") +
  theme_sjplot2() +
  scale_fill_simpsons() +
  theme(legend.position = "bottom",
        text = element_text(size = fs), # determine fs
        axis.text.x = element_text(angle = 45, hjust = 1) # rotate x text
        )


```


```{r}
corpus_plutchik %>%
  filter(!is.na(emotion)) %>%
  ggplot(aes(emotion, fill = type)) +
  geom_histogram(stat = "count", position = "dodge") +
  facet_wrap(. ~ title, scales = "free_y")  +
  theme_sjplot2() +
  scale_fill_simpsons() +
  theme(legend.position = "bottom",
        text = element_text(size = fs), # determine fs
        axis.text.x = element_text(angle = 45, hjust = 1) # rotate x text
        )

```

## Sentiart

```{r}
corpus_SentiArt <- corpus_all_entities_long %>%
  mutate(word = tolower(word)) %>%
  anti_join(stop_german, by = "word")

corpus_SentiArt <-  left_join(corpus_SentiArt, sentiart, by = "word")

summary(corpus_SentiArt)
```

### fear

```{r fig.height=7, fig.width=10}
corpus_SentiArt %>% 
  ggplot(aes(type, fear_z, fill = type)) +
  geom_boxplot() +
  theme_sjplot2() +
  scale_fill_simpsons()     +
  ggpubr::stat_compare_means(method = "wilcox.test",
                             comparisons = list(c("CH_rural", "CH_urban")),
                             na.rm = T,
                             label = "p.signif")

```
```{r}

Rmisc::summarySE(corpus_SentiArt, measurevar = "fear_z",
          groupvars = c("type"),
          na.rm = TRUE,
          conf.interval = 0.95)

```

```{r}
compare_means(fear_z ~ type, data = corpus_SentiArt, method = "wilcox.test")

```

### disgust

```{r fig.height=7, fig.width=10}

corpus_SentiArt %>% 
  ggplot(aes(type, disg_z, fill = type)) +
  geom_boxplot() +
  theme_sjplot2() +
  scale_fill_simpsons()     +
  ggpubr::stat_compare_means(method = "wilcox.test",
                             comparisons = list(c("CH_rural", "CH_urban")),
                             na.rm = T,
                             label = "p.signif")
```
```{r}

Rmisc::summarySE(corpus_SentiArt, measurevar = "disg_z",
          groupvars = c("type"),
          na.rm = TRUE,
          conf.interval = 0.95)

```

```{r}
compare_means(disg_z ~ type, data = corpus_SentiArt, method = "wilcox.test")

```

### happyness

```{r fig.height=7, fig.width=10}

corpus_SentiArt %>% 
  ggplot(aes(type, hap_z, fill = type)) +
  geom_boxplot() +
  theme_sjplot2() +
  scale_fill_simpsons()     +
  ggpubr::stat_compare_means(method = "wilcox.test",
                             comparisons = list(c("CH_rural", "CH_urban")),
                             na.rm = T,
                             label = "p.signif")
```
```{r}

Rmisc::summarySE(corpus_SentiArt, measurevar = "hap_z",
          groupvars = c("type"),
          na.rm = TRUE,
          conf.interval = 0.95)

```

```{r}
compare_means(hap_z ~ type, data = corpus_SentiArt, method = "wilcox.test")

```

### sadness

```{r fig.height=7, fig.width=10}

corpus_SentiArt %>% 
  ggplot(aes(type, sad_z, fill = type)) +
  geom_boxplot() +
  theme_sjplot2() +
  scale_fill_simpsons()     +
  ggpubr::stat_compare_means(method = "wilcox.test",
                             comparisons = list(c("CH_rural", "CH_urban")),
                             na.rm = T,
                             label = "p.signif")
```
```{r}

Rmisc::summarySE(corpus_SentiArt, measurevar = "sad_z",
          groupvars = c("type"),
          na.rm = TRUE,
          conf.interval = 0.95)

```

```{r}
compare_means(sad_z ~ type, data = corpus_SentiArt, method = "wilcox.test")

```

### surprise

```{r fig.height=7, fig.width=10}

corpus_SentiArt %>% 
  ggplot(aes(type, surp_z, fill = type)) +
  geom_boxplot() +
  theme_sjplot2() +
  scale_fill_simpsons()     +
  ggpubr::stat_compare_means(method = "wilcox.test",
                             comparisons = list(c("CH_rural", "CH_urban")),
                             na.rm = T,
                             label = "p.signif")
```
```{r}

Rmisc::summarySE(corpus_SentiArt, measurevar = "surp_z",
          groupvars = c("type"),
          na.rm = TRUE,
          conf.interval = 0.95)

```

```{r}
compare_means(surp_z ~ type, data = corpus_SentiArt, method = "wilcox.test")

```

### anger

```{r fig.height=7, fig.width=10}

corpus_SentiArt %>% 
  ggplot(aes(type, ang_z, fill = type)) +
  geom_boxplot() +
  theme_sjplot2() +
  scale_fill_simpsons()     +
  ggpubr::stat_compare_means(method = "wilcox.test",
                             comparisons = list(c("CH_rural", "CH_urban")),
                             na.rm = T,
                             label = "p.signif")
```
```{r}

Rmisc::summarySE(corpus_SentiArt, measurevar = "ang_z",
          groupvars = c("type"),
          na.rm = TRUE,
          conf.interval = 0.95)

```

```{r}
compare_means(ang_z ~ type, data = corpus_SentiArt, method = "wilcox.test")

```


```{r}
corpus_all_entities_long %>%
  # mutate(word = tolower(word)) %>%
  select(5, 7) %>%
  group_by(word, type) %>% 
  anti_join(stop_german, by = "word") %>%
  inner_join(sentiart_long, by = "word")  %>%
  # summarise(value = mean(value)) %>%
  ggplot(aes(x = type, y = value, fill = emotion)) +
  ylim(-2,2) +
  # facet_wrap(~ type, scales = "free_y") +
  geom_boxplot() +
  theme_sjplot2() +
  theme(legend.position = 'none', # get rid of legend
        axis.text.x = element_text(angle = 45, hjust = 1, size = fs/1.5)) + 
  scale_fill_simpsons() +
  facet_grid(emotion ~ .)
```



