---
title: "Test paper - corpus prep"
author: "Giulia Grisot"
date: "2020"
output:
  html_notebook: 
    number_sections: no
    theme: flatly
---

```{r message=FALSE, warning=F}

library(tidyverse)
library(tidytext)
library(sjPlot)
library(ggsci)
# library(wesanderson)
library(wordcloud)
library(readtext)
library(readxl)

```

# Corpus preparation

## Load txt files from a directory

```{r}

# read in texts (file name must be in the format: surname_title_year.txt)

# for instructions about how to see:  https://data.library.virginia.edu/a-beginners-guide-to-text-analysis-with-quanteda/
# corpus_source <- as.data.frame(readtext("1_corpus/*.txt",

#                       docvarsfrom = "filenames",
#                       docvarnames = c("author", "title", "year"),
#                       dvsep = "_",
#                       encoding = "UTF-8"))
# 
# corpus_source <- corpus_source %>%
#   dplyr::mutate(doc_id = row_number())
# 

corpus_source <- as.data.frame(readtext("/Users/jberenike/GitHub/test_paper_swiss/berenike_sentiment_youth/Grimm/7th_Edition/*.txt", encoding = "UTF-8"))

corpus_source2 <- corpus_source %>%
  dplyr::mutate(doc_id1 = row_number())

# write.csv(corpus_source, "corpus_source.csv", fileEncoding = "UTF-8")

```

## Transform into flat corpus

```{r}

text_all <- corpus_source2

text_all$doc_id <- str_replace(text_all$doc_id, ".txt", "")

text_all <- text_all %>%
unnest_tokens(sentence, text, token = 'sentences', to_lower = F)

#if split by words instead, it might be necessary to add fake sections to see sentiments curve along the book. this can be done as  follows (to make 10 sections per book)

# text_all %>%
#   group_by(book) %>%
#   mutate(section = cut(row_number(), breaks = 10, labels = FALSE))

```

## Stop words

A next step would be to examine word frequencies.

- let's start by making a dataset of german stop words that will then be removed from the corpus

```{r}
stop_german <- tibble(word = stopwords::stopwords("de"))
stop_french <- tibble(word = stopwords::stopwords("fr"))
stop_ita <- tibble(word = stopwords::stopwords("it"))
```

# add sentence case stopwords

```{r}
stop_german2 <- stop_german
stop_german2$word <- str_to_sentence(stop_german2$word)
stop_german <- bind_rows(stop_german, stop_german2)
remove(stop_german2)
```

## Add word ID and Frequencies 

```{r}
text_all <- text_all %>%
  group_by(doc_id) %>%
  mutate(sentence_id = row_number())

# text_all <-  text_all %>%
#   group_by(word) %>%
#   dplyr::mutate(freq = n())


text_all$book <- text_all$doc_id

text_all$doc_id <- NULL

```


```{r}
## Load txt files from a directory and prepare text corpus
# text_all <- text_all %>% filter(!(str_detect(word, "\\d"))) #remove rows containing numbers in the word column

```


```{r}
# ## indentify proper names
# word <- c("text_all", "öhi", "clara", "peter", "klara", "großmutter", "großvater", "großmama", "sesemann", "rottenmeier", "sebastian")
# text_all_names <- as.data.frame(word)
# remove(word)

```


## Remove stopwords

<!-- ```{r fig.height=7, fig.width=12, message=FALSE, warning=FALSE} -->
<!-- fs = 12 # default plot font size -->

<!-- library(tm) -->

<!-- text_all$sentence <- removeWords(text_all$sentence, stopwords(kind = "de")) -->
<!-- text_all$sentence <- removePunctuation(text_all$sentence) -->
<!-- text_all$sentence <- removeNumbers(text_all$sentence) -->

<!-- ``` -->

## Most frequent words by book plot

```{r fig.height=5, fig.width=10, message=FALSE, warning=FALSE}
fs = 12 # default plot font size


text_all %>%
  group_by(book, sentence) %>%
  count() %>%
# summarize count per word per book
  arrange(desc(n)) %>%
# highest freq on top
  group_by(book) %>% # 
  mutate(top = seq_along(word)) %>%  # identify rank within group
  filter(top <= 15) %>%
  arrange(desc(top))

# retain top 15 frequent words
  # create barplot
  # ggplot(aes(x = -top, fill = as.factor(book))) + 
  # geom_bar(aes(y = n), stat = 'identity', col = 'black') +
  # # make sure words are printed either in or next to bar
  # geom_text(aes(y = ifelse(n > max(n) / 2, max(n) / 50, n + max(n) / 50),
  #               label = word), size = fs/3, hjust = "left") +
  # theme_sjplot2() +
  # theme(legend.position = 'none', # get rid of legend
  #       axis.text.x = element_text(angle = 45, hjust = 1, size = fs/1.5), # rotate x text
  #       axis.ticks.y = element_blank(), # remove y ticks
  #       axis.text.y = element_blank()) + # remove y text
  # labs(y = "Word count", x = "", # add labels
  #      title = "Most frequent words throughout works") +
  # facet_wrap(. ~ book) + # separate plot for each section
  # coord_flip() + # flip axes
  # scale_fill_sjplot()
  
```


# Sentiment Dictionaries

## SentiWS

let's alter the SentiWS dictionary to include all forms of the different tokens

```{r}

sentiWS <- pradadata::sentiws
sentiWS_long <- unnest_tokens(sentiWS, word2, inflections, to_lower = F)

# there are some empty rows in word2 column, which should be the same as word. let's fill the gaps.

sentiWS_long1 <- sentiWS_long %>%
  select(4,1,3) %>%
  mutate(word = word2) %>%
  select(-word2)

sentiWS_long2 <- sentiWS_long %>%
  select(2,1,3)

# sentiWS_long$word <- tolower(sentiWS_long$word2)

sentiWS_long <- bind_rows(sentiWS_long2, sentiWS_long1)

sentiWS_long <- sentiWS_long %>%
  dplyr::rename(SentiWS_neg_pos = neg_pos) %>%
  dplyr::rename(SentiWS_polarity = value)

remove(sentiWS, sentiWS_long1, sentiWS_long2)


```

## Glex

```{r}
glex <- pradadata::germanlex
glex <- glex %>%
  dplyr::rename(glex_neg_pos = qualifier) %>%
  dplyr::rename(glex_polarity = polarity_strength)

# there seem to be a few words that are not right in the dataset. let's take them out

glex <- filter(glex, word != "%%")

```

## SentiART

```{r}
sentiart <- read.csv("SA_resources/SentiArt.dat", dec = ",")

sentiart_long <- sentiart %>%
  select(-1, -AAPz) %>%
  gather(emotion, value, -word)

sentiart_long_top <- sentiart_long %>% 
  group_by(word) %>% 
  slice_max(value)

```

## Plutchnik

```{r, message=F}

plutchik <- read_csv("SA_resources/Plutchik_Emotionslexikon.csv")

plutchik <- plutchik %>%
  filter(!is.na(Wortart)) %>%
  filter(!is.na(word))

plutchik$word <- plutchik$`#Term`
plutchik$emotion <- plutchik$`Emotion 1`

plutchik$`#Term` <- NULL
plutchik$`Emotion 1` <- NULL

plutchik <- plutchik %>%
  filter(emotion != "??" & emotion != "??emotion??")

plutchik$emotion <- as.factor(plutchik$emotion)

```

## LANG

```{r, message=F}
LANG_processed <- read_table2("SA_resources/LANG_processed.csv")

```

## BAWL

```{r, message=F}
BAWL <- read_csv("SA_resources/BAWL-R.csv")

CapStr <- function(y) {
  c <- strsplit(y, " ")[[1]]
  paste(toupper(substring(c, 1,1)), substring(c, 2),
        sep="", collapse=" ")
}

for(i in 1:length(BAWL$WORD)){
  
  if(BAWL$WORD_CLASS[i] == "N")
    BAWL$WORD_LOWER[i] <- CapStr(BAWL$WORD_LOWER[i])
  
}

BAWL_emotions <- data.frame(word = BAWL$WORD_LOWER, valence = BAWL$EMO_MEAN, arousal = BAWL$AROUSAL_MEAN, imageability = BAWL$IMAGE_MEAN, stringsAsFactors = F)


```

## Klinger

```{r, warning=F, message=F}

ekel <- read_table("/Users/jberenike/GitHub/test_paper_swiss/berenike_sentiment_youth/Klinger_emotion_lexicon/Ekel.txt", col_names = F) %>%
  mutate(emotion = "ekel", word = X1) %>%
  select(-X1)
freude <- read_csv("/Users/jberenike/GitHub/test_paper_swiss/berenike_sentiment_youth/Klinger_emotion_lexicon/Freude.txt", col_names = F)%>%
  mutate(emotion = "freude", word = X1) %>%
  select(-X1)
furcht <- read_csv("/Users/jberenike/GitHub/test_paper_swiss/berenike_sentiment_youth/Klinger_emotion_lexicon/Furcht.txt", col_names = F)%>%
  mutate(emotion = "furcht", word = X1) %>%
  select(-X1)
trauer <- read_csv("/Users/jberenike/GitHub/test_paper_swiss/berenike_sentiment_youth/Klinger_emotion_lexicon/Trauer.txt", col_names = F)%>%
  mutate(emotion = "trauer", word = X1) %>%
  select(-X1)
ueberraschung <- read_csv("/Users/jberenike/GitHub/test_paper_swiss/berenike_sentiment_youth/Klinger_emotion_lexicon/Ueberraschung.txt", col_names = F)%>%
  mutate(emotion = "ueberraschung", word = X1) %>%
  select(-X1)
verachtung <- read_csv("/Users/jberenike/GitHub/test_paper_swiss/berenike_sentiment_youth/Klinger_emotion_lexicon/Verachtung.txt", col_names = F)%>%
  mutate(emotion = "verachtung", word = X1) %>%
  select(-X1)
wut <- read_csv("/Users/jberenike/GitHub/test_paper_swiss/berenike_sentiment_youth/Klinger_emotion_lexicon/wut.txt", col_names = F)%>%
  mutate(emotion = "wut", word = X1) %>%
  select(-X1)

klinger <- bind_rows(ekel, freude, furcht, trauer, ueberraschung, verachtung, wut)

remove(ekel, freude, furcht, trauer, ueberraschung, verachtung, wut)
```




# Geolocations & NER

## swiss places

```{r}
library(readxl)
swiss_places_source <- read_excel("CH/swiss_places.xlsx",  sheet = "Sheet1",
                           col_types = c("skip", "text", "text", 
                                         "text", "numeric", "numeric", "text", 
                                         "text", "text", "text", "text", "numeric", 
                                         "numeric", "numeric", "numeric", 
                                         "numeric", "skip", "skip", "skip", 
                                         "skip"))
```

```{r}
swiss_places <- swiss_places_source %>%
  dplyr::select(name_1, name_2, name_3, type)


swiss_places1  <- swiss_places %>%
  unnest_tokens(name, name_1, token = "words", to_lower = F) %>%
  select(type, name)

swiss_places2  <- swiss_places %>%
  unnest_tokens(name, name_2, token = "words", to_lower = F)  %>%
  select(type, name)

swiss_places3  <- swiss_places %>%
  unnest_tokens(name, name_3, token = "words", to_lower = F)  %>%
  select(type, name)

swiss_places <- bind_rows(swiss_places1, swiss_places2, swiss_places3)

remove(swiss_places1, swiss_places2, swiss_places3)


# swiss_places <- swiss_places %>%
#   dplyr::filter(!grepl("\\(", name)) %>%
#   dplyr::filter(!grepl("\\)", name)) %>%
#   dplyr::filter(!grepl("\\d", name)) %>%
#   dplyr::filter(!grepl("/", name)) %>%
#   dplyr::filter(!grepl("&", name)) %>%
#   dplyr::filter(!grepl("\\[", name)) %>%
#   dplyr::filter(!grepl("\\]", name))


swiss_places <- swiss_places %>%
  filter(!is.na(name))  %>%
  filter(name != "-")


# swiss_places <- swiss_places %>%
#   tidytext::unnest_tokens(name, name, token = "words", to_lower = F)

 swiss_places <- swiss_places %>%
   dplyr::filter(!is.na(name))
 
 swiss_places <- swiss_places %>%
    dplyr::filter(!grepl("\\d", name))
 
 swiss_places <- swiss_places %>%
    dplyr::filter(name != "Mann" &
                     name != "Q" &
                     name != "Frau" &
                     name != "Frauen" &
                     name != "Drei" &
                     name != "Tisch" &
                     name != "gezerrt" &
                     name != "David" &
                     name != "Rolle" &
                     name != "Joseph" &
                     name != "Alte" &
                     name != "Jungen" &
                     name != "Don" &
                     name != "Donna" &
                     name != "Maria" &
                     name != "Tal" &
                     name != "Erstes" &
                     name != "B" &
                     name != "Heinrich" &
                     name != "Garten" & 
                     name != "Lee" & 
                     name != "Mittel" & 
                     name != "Art" & 
                     name != "Wagen" & 
                     name != "Speck" & 
                     name != "Morgen" & 
                     name != "Schönen" & 
                     name != "Mitte" & 
                     name != "Buch" & 
                     name != "Plan" & 
                     name != "Alter" & 
                     name != "Luft" & 
                     name != "Erste" & 
                     name != "Enge" & 
                     name != "Stock" & 
                     name != "Gottes" & 
                     name != "Vogel" & 
                     name != "Schule" & 
                     name != "Wasser" & 
                     name != "Lohn" & 
                     name != "Brot" & 
                     name != "Nie" & 
                     name != "Grauen" & 
                     name != "Kleine" & 
                     name != "Laufen" & 
                     name != "Jakob" & 
                     name != "Auge" & 
                     name != "Jungen" & 
                     name != "Spiegel" & 
                     name != "Meyer" & 
                     name != "Loch" & 
                     name != "Innere" & 
                     name != "Leid" & 
                     name != "Teilen" & 
                     name != "Mauer" & 
                     name != "Mut" & 
                     name != "Ei" & 
                     name != "Arten" & 
                     name != "Ring" & 
                     name != "Aussicht" & 
                     name != "Zug" & 
                     name != "B" & 
                     name != "Felix" & 
                     name != "Inhalte" & 
                     name != "Tante" & 
                     name != "Margot" & 
                     name != "Anna" & 
                     name != "Dritte" & 
                     name != "Ach" & 
                     name != "Beim" & 
                     name != "Rosa" & 
                     name != "Jean" & 
                     name != "Frohe" & 
                     name != "U" & 
                     name != "Schwarz" & 
                     name != "Michael" & 
                     name != "Peter" & 
                     name != "Sebastian" & 
                     name != "Hund" & 
                     name != "Marc" & 
                     name != "Signora" & 
                     name != "Valentino" & 
                     name != "Piano" & 
                     name != "Zweites" & 
                     name != "Viertes" & 
                     name != "Nase" & 
                     name != "Base" & 
                     name != "Kuchen" & 
                     name != "Satz" & 
                     name != "Gips" & 
                     name != "Roten" & 
                     name != "Krone" & 
                     name != "Rot" & 
                     name != "Gelb" & 
                     name != "Rad" & 
                     name != "Prosa" & 
                     name != "Lag" & 
                     name != "Bestellung" & 
                     name != "Mein" & 
                     name != "Vater" & 
                     name != "Bruder" & 
                     name != "Zeit" & 
                     name != "Numa" & 
                     name != "West" & 
                     name != "Ost" & 
                     name != "Ab" & 
                     name != "B" & 
                     name != "Ach")

```


````{r}

swiss_places$name <- tolower(swiss_places$name)


swiss_places <- swiss_places %>% dplyr::anti_join(stop_german, by = c("name" = "word"))
swiss_places <- swiss_places %>% dplyr::anti_join(stop_ita, by = c("name" = "word"))
swiss_places <- swiss_places %>% dplyr::anti_join(stop_french, by = c("name" = "word"))


swiss_places <- distinct(swiss_places)



swiss_places_wide <- swiss_places %>%
  tidyr::pivot_wider(values_from = "type", names_from="type")

names(swiss_places_wide)[2:9] <- c("type1", "type2", "type3", "type4", "type5", "type6", "type7", "type8")

swiss_places_wide$name <- str_to_title(swiss_places_wide$name)
# swiss_places$geo_loc = "GPE"

swiss_places_wide <- swiss_places_wide %>%
   filter(!str_detect(name, "\\."))

swiss_places <- swiss_places %>%
   filter(!str_detect(name, "\\."))

swiss_places$name <- str_to_title(swiss_places$name)

# swiss_places_wide <- swiss_places_wide %>% dplyr::anti_join(removables)

swiss_places_list <- swiss_places_wide$name

jsonlite::write_json(swiss_places_list, "swiss_gpe.json")

```


## geological/natural terms

german terms from openthesaurus, modified url for different categories (29, 5, 6)

https://www.openthesaurus.de/term/list?max=1705&offset=0&categoryId=6


```{r}
# geogr_terms <- geogr_terms <- read_excel("Geolocation and maps/geogr_terms.xlsx", 
#                                          sheet = "All_nodoub", col_types = c("text", 
#                                                                              "skip", "text"))
# geogr_terms <- read_excel("Geolocation and maps/geogr_terms.xlsx",
#                                          sheet = "Geologie")

nat_terms <- read_excel("Geolocation and map data/geogr_terms.xlsx",
                                         sheet = "Selected_with_TB")

nat_terms <- nat_terms %>%
   dplyr::filter(!is.na(word)) %>%
   dplyr::filter(!grepl("\\d", word))

nat_terms <- nat_terms %>%
   dplyr::filter(word != "Mann" &
                    word != "Q" &
                    word != "Frau" &
                    word != "Frauen" &
                    word != "Drei" &
                    word != "Tisch" &
                    word != "gezerrt" &
                    word != "David" &
                    word != "Rolle" &
                    word != "Joseph" &
                    word != "Alte" &
                    word != "Jungen" &
                    word != "Don" &
                    word != "Donna" &
                    word != "Maria" &
                    word != "Tal" &
                    word != "Erstes" &
                    word != "B" &
                    word != "Heinrich" &
                    word != "Garten" & 
                    word != "Lee" & 
                    word != "Mittel" & 
                    word != "Art" & 
                    word != "Wagen" & 
                    word != "Speck" & 
                    word != "Morgen" & 
                    word != "Schönen" & 
                    word != "Mitte" & 
                    word != "Buch" & 
                    word != "Plan" & 
                    word != "Alter" & 
                    word != "Luft" & 
                    word != "Erste" & 
                    word != "Enge" & 
                    word != "Stock" & 
                    word != "Gottes" & 
                    word != "Vogel" & 
                    word != "Schule" & 
                    word != "Wasser" & 
                    word != "Lohn" & 
                    word != "Brot" & 
                    word != "Nie" & 
                    word != "Grauen" & 
                    word != "Kleine" & 
                    word != "Laufen" & 
                    word != "Jakob" & 
                    word != "Auge" & 
                    word != "Jungen" & 
                    word != "Spiegel" & 
                    word != "Meyer" & 
                    word != "Loch" & 
                    word != "Innere" & 
                    word != "Leid" & 
                    word != "Teilen" & 
                    word != "Mauer" & 
                    word != "Mut" & 
                    word != "Ei" & 
                    word != "Arten" & 
                    word != "Ring" & 
                    word != "Aussicht" & 
                    word != "Zug" & 
                    word != "B" & 
                    word != "Felix" & 
                    word != "Inhalte" & 
                    word != "Tante" & 
                    word != "Margot" & 
                    word != "Anna" & 
                    word != "Dritte" & 
                    word != "Ach" & 
                    word != "Beim" & 
                    word != "Rosa" & 
                    word != "Jean" & 
                    word != "Frohe" & 
                    word != "U" & 
                    word != "Schwarz" & 
                    word != "Michael" & 
                    word != "Peter" & 
                    word != "Sebastian" & 
                    word != "Hund" & 
                    word != "Marc" & 
                    word != "Signora" & 
                    word != "Valentino" & 
                    word != "Piano" & 
                    word != "Zweites" & 
                    word != "Viertes" & 
                    word != "Nase" & 
                    word != "Base" & 
                    word != "Kuchen" & 
                    word != "Satz" & 
                    word != "Gips" & 
                    word != "Roten" & 
                    word != "Krone" & 
                    word != "Rot" & 
                    word != "Gelb" & 
                    word != "Rad" & 
                    word != "Prosa" & 
                    word != "Lag" & 
                    word != "Bestellung" &
                    word != "Vater" & 
                    word != "Mein" & 
                    word != "Bruder" & 
                    word != "Zeit" & 
                    word != "Numa" & 
                    word != "West" & 
                    word != "Ost" & 
                    word != "Ab" & 
                    word != "B" & 
                    word != "Ach") 


# natural_features_from_Text_Berg <- read_csv("natura features from Text+Berg.csv", 
#                                            col_types = cols(rank = col_skip(), `count T+B` = col_skip()))
# 
# T_B_list <- natura_features_from_Text_Berg$word

# geogr_terms <- geogr_terms %>%
#   unnest_tokens(word, geologie)  %>%
#   distinct() %>%
#   mutate(geo_term = "yes")


```



```{r}
nat_terms_list <- nat_terms$word

# nat_terms_list <- c(nat_terms_list,T_B_list)

# geo_all <- append(geo_all, swiss_places$name)
  
# jsonlite::write_json(geo_all, "geo_all.json")
```



# check entities

let's have a look if any items appear both in the rural lists and in the urban

```{r}
swiss_places_wide <- swiss_places_wide %>%
  mutate(urban = ifelse(type1 == "S" | type5 == "A" |  type6 == "R" | type2 == "P" , "yes", "no")) %>%
  mutate(rural = ifelse(type3 == "T" | type4 == "H" |  type7 == "L" | type8 == "V" , "yes", "no"))
```

```{r}
check <- swiss_places_wide %>%
  filter(urban == "yes" & rural == "yes")
```

they do: it's `r nrow(check)` items are in both lists, out of `r nrow(swiss_places_wide)`, meaning `r nrow(check)*100 / nrow(swiss_places_wide)` percent.



# vector lists of Swiss places by type

```{r}
CH_country_regions <- swiss_places %>%
  filter(type == "A")
CH_country_regions <- CH_country_regions$name

CH_streams_lake <- swiss_places %>%
  filter(type == "H")
CH_streams_lake <- CH_streams_lake$name

CH_park_areas <- swiss_places %>%
  filter(type == "L")
CH_park_areas <- CH_park_areas$name

CH_city_village <- swiss_places %>%
  filter(type == "P")
CH_city_village <- CH_city_village$name

CH_roads <- swiss_places %>%
  filter(type == "R")
CH_roads <- CH_roads$name

CH_building_spots <- swiss_places %>%
  filter(type == "S")
CH_building_spots <- CH_building_spots$name

CH_mountain_hill <- swiss_places %>%
  filter(type == "T")
CH_mountain_hill <- CH_mountain_hill$name

CH_forests <- swiss_places %>%
  filter(type == "V")
CH_forests <- CH_forests$name


```

# vector lists of Swiss places urban vs. rural


```{r}
# CH_urban <- swiss_places %>%
#   filter(type == "A" | type == "P" | type == "R" | type == "S") %>%
#    select("name") %>%
#    distinct()


# CH_rural <- swiss_places %>%
#   filter(type == "H" | type == "T" | type == "L" | type == "V" | type == "nat_term") %>%
#    select("name") %>%
#    distinct()




CH_urban <- swiss_places_wide %>%
  filter(urban == "yes" & is.na(rural)) %>%
   select("name") %>%
   distinct()


CH_rural <- swiss_places_wide %>%
  filter(is.na(urban) & rural == "yes") %>%
   select("name") %>%
   distinct()


CH_rural <- CH_rural$name
CH_urban <- CH_urban$name

```