---
title: "Test paper - sentiments"
author: "Giulia Grisot"
date: "2020"
output:
  html_notebook: 
    theme: flatly
    fig_width: 8
    fig_height: 5
---

# Corpus preparation

```{r message=FALSE, warning=F}
library(tidyverse)
# library(harrypotter)
library(lme4)
library(lmerTest)
library(tidytext)
library(sjPlot)
library(ggplot2)
library(ggsci)
library(ggpubr)
library(wesanderson)

```

# make corpus by word 

```{r}
 heidi_all_entities_long <- heidi_all_entities %>%
  unnest_tokens(word, text, to_lower = F) %>%
  group_by(doc_id) %>%
  dplyr::mutate(word_id = row_number()) %>%
  group_by(word) %>%
  dplyr::mutate(frequency = n()) %>%
  ungroup()

heidi_all_entities_long$type <- as.factor(heidi_all_entities_long$type)
heidi_all_entities_long$title <- as.factor(heidi_all_entities_long$title)

heidi_all_entities_long <- heidi_all_entities_long %>%
  mutate(type_grouped = ifelse(type == "nat_terms" | type == "rural" | type == "geoloc_nat", "NAT", "OTHER"))

```


## distribution of entities in the Entity lists

```{r}
all_entities %>%
  dplyr::mutate(type = label) %>%
  ggplot(aes(type, fill=type)) +
  geom_histogram(stat = "count") +
  theme_minimal()


```

## distrbution of entites in the corpus

```{r}
heidi_all_entities %>%
  group_by(title, doc_id) %>%
  ggplot(aes(type, fill=type)) +
  geom_histogram(stat = "count") +
  theme_minimal() 

```

# frequency per book

```{r}
heidi_all_entities_long[,c("title","word")]  %>%
  group_by(title, word) %>% 
  anti_join(heidi_names, by = "word") %>%  anti_join(stop_german, by = "word") %>% # delete stopwords
  count() %>% # summarize count per word per title
  arrange(desc(n)) # %>% # highest frequency on top
  # group_by(title) %>% 
  # mutate(top = seq_along(word)) %>% # identify rank within group
  # filter(top <= 15) %>% # retain top 15 frequent words
  # # create barplot
  # ggplot(aes(x = -top, fill = title)) +
  # geom_bar(aes(y = n), stat = 'identity', col = 'black') +
  # # make sure words are printed either in or next to bar
  # geom_text(aes(y = ifelse(n > max(n) / 2, max(n) / 50, n + max(n) / 50),
  #               label = word), size = fs/3, hjust = "left") +
  # theme_minimal() +
  # theme(legend.position = 'none', # get rid of legend
  #       text = element_text(size = fs), # determine fs
  #       axis.text.x = element_text(angle = 45, hjust = 1, size = fs/1.5), # rotate x text
  #       axis.ticks.y = element_blank(), # remove y ticks
  #       axis.text.y = element_blank()) + # remove y text
  # labs(y = "Word count", x = "", # add labels
  #      title = "Most frequent words by book") +
  # facet_grid(. ~ title) + # separate plot for each book
  # coord_flip() + # flip axes
  # # scale_fill_hp(discrete = T, option = "Always")


```

# frequency per entity type

```{r}

heidi_all_entities_long[,c("type","word")]  %>%
  group_by(type, word) %>%
  anti_join(heidi_names, by = "word") %>%  anti_join(stop_german, by = "word") %>% # delete stopwords
  count() %>% # summarize count per word per title
  arrange(desc(n)) %>% # highest frequency on top
  group_by(type)
# %>% # 
#   mutate(top = seq_along(word)) %>% # identify rank within group
#   filter(top <= 15) %>% # retain top 15 frequent words
#   # create barplot
#   ggplot(aes(x = -top, fill = type)) + 
#   geom_bar(aes(y = n), stat = 'identity', col = 'black') +
#   # make sure words are printed either in or next to bar
#   geom_text(aes(y = ifelse(n > max(n) / 2, max(n) / 50, n + max(n) / 50),
#                 label = word), size = fs/3, hjust = "left") +
#   theme_minimal() +
#   theme(legend.position = 'none', # get rid of legend
#         text = element_text(size = fs), # determine fs
#         axis.text.x = element_text(angle = 45, hjust = 1, size = fs/1.5), # rotate x text
#         axis.ticks.y = element_blank(), # remove y ticks
#         axis.text.y = element_blank()) + # remove y text
#   labs(y = "Word count", x = "", # add labels
#        title = "Most frequent words by type") +
#   facet_grid(. ~ type) + # separate plot for each book
#   coord_flip() + # flip axes
#   # scale_fill_hp(discrete = T, option = "Always")

```



# Sentiments by type

## BAWL 

### arousal

```{r}

heidi_BAWL <- heidi_all_entities_long %>%
  anti_join(heidi_names, by = "word") %>%  anti_join(stop_german, by = "word") %>%
  left_join(BAWL_emotions, by = "word")

```

```{r}
heidi_BAWL %>%
  group_by(type_grouped, title, doc_id) %>%
  ggplot(aes(type, fill = type)) +
  geom_histogram(stat = "count", na.rm = T) +
  theme_minimal()

```



if we wanted to have a "sentiment" per passage, i.e per doc_id, we should sum up the value of sentiment grouping it back 

```{r}
heidi_BAWL <- heidi_BAWL %>%
  dplyr::group_by(type_grouped, type, author, title, doc_id) %>%
  summarise(arousal = sum(arousal, na.rm = T),
            valence = sum(valence, na.rm = T), 
            imageability = sum(imageability, na.rm = T),
            frequency = mean(frequency, na.rm = T))
```


```{r}
heidi_BAWL %>%
  # summarise(value = mean(value)) %>%
  ggplot(aes(x = type, y = arousal, fill = type)) +
  # ylim(-2,2) +
  # facet_wrap(~ type, scales = "free_y") +
  geom_boxplot() +
  theme_minimal() +
  theme(axis.title.x = element_blank()) +
  ggtitle("BAWL", subtitle = "arousal") +
  stat_compare_means(method = "wilcox.test",
                     comparisons =                
                       list(c("rural", "urban"), 
                            c("rural", "nat_terms"),
                            c("urban", "nat_terms"),
                            c("geoloc_nat", "urban"),
                            c("geoloc_nat", "rural"),
                            c("geoloc_nat", "nat_terms"),
                            c("geoloc_loc", "geoloc_nat"),
                            c("geoloc_loc", "urban"),
                            c("geoloc_loc", "rural"),
                            c("geoloc_loc", "nat_terms")),
                     na.rm = T,
                     label = "p.signif")


```

#### summary

```{r}

Rmisc::summarySE(heidi_BAWL, measurevar = "arousal",
          groupvars = c("type"),
          na.rm = TRUE,
          conf.interval = 0.95)

```

#### compare means

```{r}

compare_means(arousal ~ type, data = heidi_BAWL, method = "wilcox")

```

#### lmer

```{r}
BAWL_arousal_heidi_lmer <- lmer(arousal ~ type + 
                            (1|title) + 
                            (1|frequency),
                          heidi_BAWL, REML = F)

```

```{r}
anova(BAWL_arousal_heidi_lmer)
```


### valence (polarity)

```{r}
heidi_BAWL  %>%
  # summarise(value = mean(value)) %>%
  ggplot(aes(x = type, y = valence, fill = type)) +
  # ylim(-2,2) +
  # facet_wrap(~ type, scales = "free_y") +
  geom_boxplot() +
  theme_minimal() +
  theme(axis.title.x = element_blank()) +
  ggtitle("BAWL", subtitle = "valence") +
  stat_compare_means(method = "wilcox.test",
                     comparisons =                
                       list(c("rural", "urban"), 
                            c("rural", "nat_terms"),
                            c("urban", "nat_terms"),
                            c("geoloc_nat", "urban"),
                            c("geoloc_nat", "rural"),
                            c("geoloc_nat", "nat_terms"),
                            c("geoloc_loc", "geoloc_nat"),
                            c("geoloc_loc", "urban"),
                            c("geoloc_loc", "rural"),
                            c("geoloc_loc", "nat_terms")),
                     na.rm = T,
                     label = "p.signif")

```

#### summary

```{r}

Rmisc::summarySE(heidi_BAWL, measurevar = "valence",
          groupvars = c("type"),
          na.rm = TRUE,
          conf.interval = 0.95)

```

#### compare means

```{r}

compare_means(valence ~ type, data = heidi_BAWL, method = "wilcox.test")


```

#### lmer

```{r}
BAWL_valence_heidi_lmer <- lmer(valence ~ type + 
                            (1|frequency) +
                            (1|title),
                          heidi_BAWL, REML = F)

```

```{r}
anova(BAWL_valence_heidi_lmer)

```

### imageability

```{r}
heidi_BAWL  %>%
  # summarise(value = mean(value)) %>%
  ggplot(aes(x = type, y = imageability, fill = type)) +
  # ylim(-2,2) +
  # facet_wrap(~ type, scales = "free_y") +
  geom_boxplot() +
  theme_minimal() +
  theme(axis.title.x = element_blank()) +
  ggtitle("BAWL", subtitle = "imageability") +
  # if unified nat_term and CH_rural
  stat_compare_means(method = "wilcox.test",
                     comparisons =                
                       list(c("rural", "urban"), 
                            c("rural", "nat_terms"),
                            c("urban", "nat_terms"),
                            c("geoloc_nat", "urban"),
                            c("geoloc_nat", "rural"),
                            c("geoloc_nat", "nat_terms"),
                            c("geoloc_loc", "geoloc_nat"),
                            c("geoloc_loc", "urban"),
                            c("geoloc_loc", "rural"),
                            c("geoloc_loc", "nat_terms")),
                     na.rm = T,
                     label = "p.signif")

```

#### summary

```{r}

Rmisc::summarySE(heidi_BAWL, measurevar = "imageability",
          groupvars = c("type"),
          na.rm = TRUE,
          conf.interval = 0.95)

```

#### compare means

```{r}

compare_means(imageability ~ type, data = heidi_BAWL, method = "wilcox.test")


```

#### lmer

```{r}
BAWL_imag_heidi_lmer <- lmer(imageability ~ type +
                         (1|frequency) +
                         (1|title),
                       heidi_BAWL, REML = F)


```


```{r}

anova(BAWL_imag_heidi_lmer)

# rstatix::anova_test(heidi_BAWL, formula = imageability ~ type)
```

## SentiWS 

```{r}

heidi_sentiWS <- heidi_all_entities_long %>%
  anti_join(heidi_names, by = "word") %>%  anti_join(stop_german, by = "word") %>%
  left_join(sentiWS_long, by = "word")

```

```{r}
lowest_negative_value = min(heidi_sentiWS$SentiWS_polarity, na.rm = T)

heidi_sentiWS <- heidi_sentiWS %>%
  mutate(SentiWS_polarity = SentiWS_polarity - lowest_negative_value)

heidi_sentiWS <- heidi_sentiWS %>%
  dplyr::group_by(type_grouped, type, author, title, doc_id) %>%  
  summarise(SentiWS_polarity = sum(SentiWS_polarity, na.rm = T), frequency = mean(frequency, na.rm = T))

```

### polarity

```{r}
heidi_sentiWS %>%
  # summarise(value = mean(value)) %>%
  ggplot(aes(x = type, y = SentiWS_polarity, fill = type)) +
  # facet_wrap(~ type, scales = "free_y") +
  geom_boxplot() +
  theme_minimal() +
  theme(axis.title.x = element_blank()) +
  ggtitle("SentiWS", subtitle = "polarity") +
  stat_compare_means(comparisons =                
                       list(c("rural", "urban"), 
                            c("rural", "nat_terms"),
                            c("urban", "nat_terms"),
                            c("geoloc_nat", "urban"),
                            c("geoloc_nat", "rural"),
                            c("geoloc_nat", "nat_terms"),
                            c("geoloc_loc", "geoloc_nat"),
                            c("geoloc_loc", "urban"),
                            c("geoloc_loc", "rural"),
                            c("geoloc_loc", "nat_terms")),
                     na.rm = T,
                     label = "p.signif")

#   facet_grid(. ~ title)
```

#### summary

```{r}

Rmisc::summarySE(heidi_sentiWS, measurevar = "SentiWS_polarity",
          groupvars = c("type"),
          na.rm = TRUE,
          conf.interval = 0.95)

```

#### compare means

```{r}

compare_means(SentiWS_polarity ~ type, data = heidi_sentiWS, method = "wilcox.test")


```

#### lmer

```{r}
SentiWS_polarity_heidi_lmer <- lmer(SentiWS_polarity ~ type +
                                (1|frequency) +
                                (1|title),
                              heidi_sentiWS, REML = F)

```

```{r}
anova(SentiWS_polarity_heidi_lmer)

```

## LANG 

```{r}

heidi_LANG <- heidi_all_entities_long %>%
  anti_join(heidi_names, by = "word") %>%  anti_join(stop_german, by = "word") %>%
 left_join(select(LANG_processed, -8), by = "word")

# ks.test(heidi_LANG$arousal_mean, "pnorm", mean=mean(heidi_LANG$arousal_mean), sd=sd(heidi_LANG$arousal_mean))
# ks.test(heidi_LANG$valence_mean, "pnorm", mean=mean(heidi_LANG$valence_mean), sd=sd(heidi_LANG$valence_mean))
# 

# ggplot(heidi_LANG, aes(arousal_mean)) +
#   geom_histogram()
# ggplot(heidi_LANG, aes(valence_mean)) +
#   geom_histogram()

```

```{r}
heidi_LANG <- heidi_LANG %>%
  dplyr::group_by(type_grouped, type, author, title, doc_id, pattern) %>%
  summarise(arousal_mean = sum(arousal_mean, na.rm = T),
            valence_mean = sum(valence_mean, na.rm = T), 
            concreteness_mean = sum(concreteness_mean, na.rm = T), 
            frequency = mean(frequency, na.rm = T)
            )
```

### arousal

```{r}
heidi_LANG %>%
  # summarise(value = mean(value)) %>%
  ggplot(aes(x = type, y = arousal_mean, fill = type)) +
  # ylim(-2,2) +
  # facet_wrap(~ type, scales = "free_y") +
  geom_boxplot() +
    theme_minimal() +
  theme(axis.title.x = element_blank()) +
  ggtitle("LANG", subtitle = "arousal") +
  stat_compare_means(method = "wilcox.test",
                     comparisons =                
                       list(c("rural", "urban"), 
                            c("rural", "nat_terms"),
                            c("urban", "nat_terms"),
                            c("geoloc_nat", "urban"),
                            c("geoloc_nat", "rural"),
                            c("geoloc_nat", "nat_terms"),
                            c("geoloc_loc", "geoloc_nat"),
                            c("geoloc_loc", "urban"),
                            c("geoloc_loc", "rural"),
                            c("geoloc_loc", "nat_terms")),
                     na.rm = T,
                     label = "p.signif")

```

#### summary

```{r}

Rmisc::summarySE(heidi_LANG, measurevar = "arousal_mean",
          groupvars = c("type"),
          na.rm = TRUE,
          conf.interval = 0.95)

```

#### compare means

```{r}

compare_means(arousal_mean ~ type, data = heidi_LANG, method = "wilcox.test")


```

#### lmer

```{r}
LANG_arousal_heidi_lmer <- lmer(arousal_mean ~ type + 
                            (1|frequency) +
                            (1|title),
                          heidi_LANG, REML = F)


# summary(LANG_arousal_heidi_lmer)

```

```{r}
anova(LANG_arousal_heidi_lmer)
```



### valence

```{r}
heidi_LANG %>%
  # summarise(value = mean(value)) %>%
  ggplot(aes(x = type, y = valence_mean, fill = type)) +
  # ylim(-2,2) +
  # facet_wrap(~ type, scales = "free_y") +
  geom_boxplot() +
   theme_minimal() +
  theme(axis.title.x = element_blank()) +
  ggtitle("LANG", subtitle = "valence") +
  stat_compare_means(method = "wilcox.test",
                     comparisons =                
                       list(c("rural", "urban"), 
                            c("rural", "nat_terms"),
                            c("urban", "nat_terms"),
                            c("geoloc_nat", "urban"),
                            c("geoloc_nat", "rural"),
                            c("geoloc_nat", "nat_terms"),
                            c("geoloc_loc", "geoloc_nat"),
                            c("geoloc_loc", "urban"),
                            c("geoloc_loc", "rural"),
                            c("geoloc_loc", "nat_terms")),
                     na.rm = T,
                     label = "p.signif")

```

#### summary

```{r}

Rmisc::summarySE(heidi_LANG, measurevar = "valence_mean",
          groupvars = c("type"),
          na.rm = TRUE,
          conf.interval = 0.95)

```

#### compare means

```{r}

compare_means(valence_mean ~ type, data = heidi_LANG, method = "wilcox.test")


```

#### lmer

```{r}
LANG_valence_heidi_lmer <- lmer(valence_mean ~ type + 
                            (1|frequency) +
                            (1|title),
                          heidi_LANG, REML = F)

```

```{r}
anova(LANG_valence_heidi_lmer)
```

### concreteness

```{r}
heidi_LANG %>%
  # summarise(value = mean(value)) %>%
  ggplot(aes(x = type, y = concreteness_mean, fill = type)) +
  # ylim(-2,2) +
  # facet_wrap(~ type, scales = "free_y") +
  geom_boxplot() +
    theme_minimal() +
  theme(axis.title.x = element_blank()) +
  ggtitle("LANG", subtitle = "concreteness") +
  stat_compare_means(method = "wilcox.test",
                     comparisons =                
                       list(c("rural", "urban"), 
                            c("rural", "nat_terms"),
                            c("urban", "nat_terms"),
                            c("geoloc_nat", "urban"),
                            c("geoloc_nat", "rural"),
                            c("geoloc_nat", "nat_terms"),
                            c("geoloc_loc", "geoloc_nat"),
                            c("geoloc_loc", "urban"),
                            c("geoloc_loc", "rural"),
                            c("geoloc_loc", "nat_terms")),
                     na.rm = T,
                     label = "p.signif")

```

#### summary

```{r}

Rmisc::summarySE(heidi_LANG, measurevar = "concreteness_mean",
          groupvars = c("type"),
          na.rm = TRUE,
          conf.interval = 0.95)

```

#### compare means

```{r}

compare_means(concreteness_mean ~ type, data = heidi_LANG, method = "wilcox.test")


```

#### lmer

```{r}
LANG_concreteness_heidi_lmer <- lmer(concreteness_mean ~ type + 
                            (1|frequency) +
                            (1|title),
                          heidi_LANG, REML = F)

```

```{r}
anova(LANG_concreteness_heidi_lmer)
```

## lmer comparison

```{r}
tab_model(BAWL_arousal_heidi_lmer,
  BAWL_valence_heidi_lmer,
  BAWL_imag_heidi_lmer,
  LANG_arousal_heidi_lmer,
  LANG_valence_heidi_lmer,
  LANG_concreteness_heidi_lmer,
  SentiWS_polarity_heidi_lmer,
          show.se = T,
          show.ci = F,
          show.stat = T,
          emph.p = T,
          transform = NULL,
          string.pred = "Pred",
          string.stat = "z",
          string.se = "SE",
          show.icc = F)

```


# discrete models

## Klinger

```{r}
heidi_klinger <- heidi_all_entities_long %>%
  anti_join(heidi_names, by = "word") %>%  anti_join(stop_german, by = "word") %>%
  left_join(klinger, by = "word")

heidi_klinger$emotion <- as.factor(heidi_klinger$emotion)
```


```{r}
heidi_klinger <- heidi_klinger %>%
  mutate(emotion_count = ifelse(!is.na(emotion), 1, 0)) %>%
  dplyr::group_by(type_grouped, type, author, title, doc_id, emotion) %>%
  summarise(emotion_count = sum(emotion_count, na.rm=T),
            frequency = mean(frequency, na.rm = T))
```

### emotions

#### absolute plot

```{r}

heidi_klinger %>%
  group_by(emotion, type) %>%
  filter(!is.na(emotion)) %>%
  summarize(count = n()) %>%
  ggplot(aes(x = emotion, y = count, fill = emotion)) +    
  geom_bar(stat = 'identity') +
  theme_minimal() +
  theme(legend.position = 'none', # get rid of legend
        axis.text.x = element_text(angle = 45, hjust = 1, size = fs/1.5)) + 
  
  facet_grid(. ~ type)

```

#### proportional plot

```{r}
heidi_klinger %>%
  group_by(type) %>%
  mutate(row_n_type = n()) %>%
  group_by(type, emotion) %>%
  summarise(emotion_count = n()/row_n_type) %>%
  group_by(emotion) %>%
  distinct() %>%
  filter(!is.na(emotion)) %>%
  ggplot(aes(x = emotion, y = emotion_count, fill = emotion)) +    
  geom_bar(stat = 'identity') +
  theme_minimal() +
  theme(legend.position = 'none', # get rid of legend
        axis.text.x = element_text(angle = 45, hjust = 1, size = fs/1.5)) + 
  
  facet_grid(. ~ type)
```


<!-- ### Words carrying strongest emotions Klinger -->

<!-- ```{r fig.height=7, fig.width=10} -->

<!-- heidi_klinger %>%  -->
<!--   group_by(word, emotion, type) %>% -->
<!--   count() %>% # summarize count per word per sentiment -->
<!--   group_by(emotion) %>% -->
<!--   arrange(emotion, desc(n)) %>% # most frequent on top -->
<!--   mutate(top = seq_along(word)) %>% # identify rank within group -->
<!--   filter(top <= 15) %>% # keep top 15 frequent words -->
<!--   ggplot(aes(x = -top, fill = factor(emotion))) +  -->
<!--   # create barplot -->
<!--   geom_bar(aes(y = n), stat = 'identity', col = 'black') + -->
<!--   # make sure words are printed either in or next to bar -->
<!--   geom_text(aes(y = ifelse(n > max(n) / 2, max(n) / 50, n + max(n) / 50), -->
<!--                 label = word), size = fs/3, hjust = "left") + -->
<!--   theme_minimal() + -->
<!--   theme(legend.position = 'none', # remove legend -->
<!--         text = element_text(size = fs), # determine fs -->
<!--         axis.text.x = element_text(angle = 45, hjust = 1), # rotate x text -->
<!--         axis.ticks.y = element_blank(), # remove y ticks -->
<!--         axis.text.y = element_blank()) + # remove y text -->
<!--   labs(y = "Word count", x = "", # add manual labels -->
<!--        title = "Words carrying strongest emotions") + -->
<!--   facet_grid(. ~ emotion, scales = "free") + # separate plot for each sentiment -->
<!--   coord_flip() # flip axes -->


<!-- ``` -->


```{r}
summary(heidi_klinger)
```

```{r}

ggplot(heidi_klinger, aes(emotion, fill = type)) +
  geom_bar(stat = "count", position = "fill") +
  theme_minimal()


```

## Plutchnik

```{r}
heidi_plutchik <- heidi_all_entities_long %>%
  anti_join(heidi_names, by = "word") %>%  anti_join(stop_german, by = "word") %>%
  left_join(plutchik, by = "word")

```

```{r}
heidi_plutchik <- heidi_plutchik %>%
  mutate(emotion_count = ifelse(!is.na(emotion), 1, 0)) %>%
  dplyr::group_by(type_grouped, type, author, title, doc_id, emotion) %>%
  summarise(emotion_count = sum(emotion_count, na.rm=T),
            frequency = mean(frequency, na.rm = T))
```



### emotions

#### absolute plot

```{r}

heidi_plutchik %>%
  group_by(emotion, type) %>%
  filter(!is.na(emotion)) %>%
  summarize(count = n()) %>%
  ggplot(aes(x = emotion, y = count, fill = emotion)) +    
  geom_bar(stat = 'identity') +
  theme_minimal() +
  theme(legend.position = 'none', # get rid of legend
        axis.text.x = element_text(angle = 45, hjust = 1, size = fs/1.5)) + 
  facet_grid(. ~ type)

```
#### proportional plot

```{r}
heidi_plutchik %>%
  group_by(type) %>%
  mutate(row_n_type = n()) %>%
  group_by(type, emotion) %>%
  summarise(emotion_count = n()/row_n_type) %>%
  group_by(emotion) %>%
  distinct() %>%
  filter(!is.na(emotion)) %>%
  ggplot(aes(x = emotion, y = emotion_count, fill = emotion)) +    
  geom_bar(stat = 'identity') +
  theme_minimal() +
  theme(legend.position = 'none', # get rid of legend
        axis.text.x = element_text(angle = 45, hjust = 1, size = fs/1.5)) + 
  facet_grid(. ~ type)

```

```{r}
summary(heidi_plutchik)
```

```{r}

# heidi_plutchik <- heidi_plutchik %>%
#   group_by(type, emotion) %>%
#   mutate(emotion_proportion = n()) %>%
#   ungroup()
# 
# heidi_plutchik <- heidi_plutchik %>%
#   group_by(type) %>%
#   mutate(emotion_proportion2 = n()) %>%
#   ungroup()
# 
# heidi_plutchik <- heidi_plutchik %>%
#   mutate(emotion_proportion = emotion_proportion/emotion_proportion2*100)
# 
# heidi_plutchik$emotion_proportion2 <- NULL




ggplot(heidi_plutchik, aes(emotion, fill = type)) +
  geom_bar(stat = "count", position = "fill") +
  theme_minimal() +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank())


```

## Sentiart

```{r}
heidi_SentiArt <- heidi_all_entities_long %>%
  mutate(word = tolower(word)) %>%
  anti_join(stop_german, by = "word")

heidi_SentiArt <-  left_join(heidi_SentiArt, sentiart, by = "word")


```

## corpus with values by emotion, aggregated by doc_id

```{r}
heidi_SentiArt2 <- heidi_SentiArt %>%
  pivot_longer(12:18, names_to = "emotion", values_to = "value")

lowest_negative_value = min(heidi_SentiArt2$value, na.rm = T)

heidi_SentiArt2 <- heidi_SentiArt2 %>%
  mutate(value_scaled = value - lowest_negative_value)

heidi_SentiArt2 <- heidi_SentiArt2 %>%
  dplyr::group_by(type_grouped, type, doc_id, emotion) %>%
  summarise(value_scaled = mean(value_scaled, na.rm = T), frequency = mean(frequency, na.rm = T))

heidi_SentiArt2$type <- as.factor(heidi_SentiArt2$type)
heidi_SentiArt2$doc_id <- as.factor(heidi_SentiArt2$doc_id)
heidi_SentiArt2$emotion <- as.factor(heidi_SentiArt2$emotion)

```

## Sentiart

#### summary

```{r}

Rmisc::summarySE(heidi_SentiArt2,
                 measurevar = "value_scaled",
          groupvars = c("type", "emotion"),
          na.rm = TRUE,
          conf.interval = 0.95)

```

#### compare means

```{r}
compare_means(value_scaled ~ type, data = heidi_SentiArt2, method = "wilcox.test", group.by = "emotion")

```

#### absolute plot

```{r}
heidi_SentiArt2 %>%
  ggplot(aes(x = emotion, y = value_scaled, fill = emotion)) +    
  geom_bar(stat = 'identity') +
  theme_minimal() +
  ggtitle("SentiArt", subtitle = "absolute count") +
  theme(legend.position = 'none', # get rid of legend
        axis.text.x = element_text(angle = 45, hjust = 1, size = fs/1.5)) + 
  facet_grid(. ~ type)
```


#### proportional plot

```{r}

heidi_SentiArt2 %>%
  group_by(type) %>%
  mutate(row_n_type = n()) %>%
  group_by(type, emotion) %>%
  summarise(emotion_value = value_scaled/row_n_type) %>%
  group_by(emotion) %>%
  distinct() %>%
  filter(!is.na(emotion)) %>%
  ggplot(aes(x = emotion, y = emotion_value, fill = emotion)) +    
  geom_bar(stat = 'identity') +
  theme_minimal() +
  ggtitle("SentiArt") +
  theme(legend.position = 'none', # get rid of legend
        axis.text.x = element_text(angle = 45, hjust = 1, size = fs/1.5)) + 
  facet_grid(. ~ type)


```
## single emotions comparisons

### fear

```{r}
heidi_SentiArt2 %>%
  filter(emotion == "fear_z") %>%
  ggplot(aes(x = type, y = value_scaled, fill = type)) +
  # ylim(-2,2) +
  # facet_wrap(~ type, scales = "free_y") +
  geom_boxplot() +
  theme_minimal() +
  theme(axis.title.x = element_blank()) +
  ggtitle("sentiArt", subtitle = "fear") +
  # if unified nat_term and CH_rural
  stat_compare_means(method = "wilcox.test",
                     comparisons =                
                       list(c("rural", "urban"), 
                            c("rural", "nat_terms"),
                            c("urban", "nat_terms"),
                            c("geoloc_nat", "urban"),
                            c("geoloc_nat", "rural"),
                            c("geoloc_nat", "nat_terms"),
                            c("geoloc_loc", "geoloc_nat"),
                            c("geoloc_loc", "urban"),
                            c("geoloc_loc", "rural"),
                            c("geoloc_loc", "nat_terms")),
                     na.rm = T,
                     label = "p.signif")

```



### disgust


```{r}
heidi_SentiArt2 %>%
  filter(emotion == "disg_z") %>%
  ggplot(aes(x = type, y = value_scaled, fill = type)) +
  # ylim(-2,2) +
  # facet_wrap(~ type, scales = "free_y") +
  geom_boxplot() +
  theme_minimal() +
  theme(axis.title.x = element_blank()) +
  ggtitle("sentiArt", subtitle = "disgust") +
  # if unified nat_term and CH_rural
  stat_compare_means(method = "wilcox.test",
                     comparisons =                
                       list(c("rural", "urban"), 
                            c("rural", "nat_terms"),
                            c("urban", "nat_terms"),
                            c("geoloc_nat", "urban"),
                            c("geoloc_nat", "rural"),
                            c("geoloc_nat", "nat_terms"),
                            c("geoloc_loc", "geoloc_nat"),
                            c("geoloc_loc", "urban"),
                            c("geoloc_loc", "rural"),
                            c("geoloc_loc", "nat_terms")),
                     na.rm = T,
                     label = "p.signif")

```

### happyness


```{r}
heidi_SentiArt2 %>%
  filter(emotion == "hap_z") %>%
  ggplot(aes(x = type, y = value_scaled, fill = type)) +
  # ylim(-2,2) +
  # facet_wrap(~ type, scales = "free_y") +
  geom_boxplot() +
  theme_minimal() +
  theme(axis.title.x = element_blank()) +
  ggtitle("sentiArt", subtitle = "happiness") +
  # if unified nat_term and CH_rural
  stat_compare_means(method = "wilcox.test",
                     comparisons =                
                       list(c("rural", "urban"), 
                            c("rural", "nat_terms"),
                            c("urban", "nat_terms"),
                            c("geoloc_nat", "urban"),
                            c("geoloc_nat", "rural"),
                            c("geoloc_nat", "nat_terms"),
                            c("geoloc_loc", "geoloc_nat"),
                            c("geoloc_loc", "urban"),
                            c("geoloc_loc", "rural"),
                            c("geoloc_loc", "nat_terms")),
                     na.rm = T,
                     label = "p.signif")

```


### sadness

```{r}
heidi_SentiArt2 %>%
  filter(emotion == "sad_z") %>%
  ggplot(aes(x = type, y = value_scaled, fill = type)) +
  # ylim(-2,2) +
  # facet_wrap(~ type, scales = "free_y") +
  geom_boxplot() +
  theme_minimal() +
  theme(axis.title.x = element_blank()) +
  ggtitle("sentiArt", subtitle = "sadness") +
  # if unified nat_term and CH_rural
  stat_compare_means(method = "wilcox.test",
                     comparisons =                
                       list(c("rural", "urban"), 
                            c("rural", "nat_terms"),
                            c("urban", "nat_terms"),
                            c("geoloc_nat", "urban"),
                            c("geoloc_nat", "rural"),
                            c("geoloc_nat", "nat_terms"),
                            c("geoloc_loc", "geoloc_nat"),
                            c("geoloc_loc", "urban"),
                            c("geoloc_loc", "rural"),
                            c("geoloc_loc", "nat_terms")),
                     na.rm = T,
                     label = "p.signif")

```


### surprise


```{r}
heidi_SentiArt2 %>%
  filter(emotion == "surp_z") %>%
  ggplot(aes(x = type, y = value_scaled, fill = type)) +
  # ylim(-2,2) +
  # facet_wrap(~ type, scales = "free_y") +
  geom_boxplot() +
  theme_minimal() +
  theme(axis.title.x = element_blank()) +
  ggtitle("sentiArt", subtitle = "surprise") +
  # if unified nat_term and CH_rural
  stat_compare_means(method = "wilcox.test",
                     comparisons =                
                       list(c("rural", "urban"), 
                            c("rural", "nat_terms"),
                            c("urban", "nat_terms"),
                            c("geoloc_nat", "urban"),
                            c("geoloc_nat", "rural"),
                            c("geoloc_nat", "nat_terms"),
                            c("geoloc_loc", "geoloc_nat"),
                            c("geoloc_loc", "urban"),
                            c("geoloc_loc", "rural"),
                            c("geoloc_loc", "nat_terms")),
                     na.rm = T,
                     label = "p.signif")

```


### anger

```{r}

heidi_SentiArt2 %>%
  filter(emotion == "ang_z") %>%
  ggplot(aes(x = type, y = value_scaled, fill = type)) +
  # ylim(-2,2) +
  # facet_wrap(~ type, scales = "free_y") +
  geom_boxplot() +
  theme_minimal() +
  theme(axis.title.x = element_blank()) +
  ggtitle("sentiArt", subtitle = "anger") +
  # if unified nat_term and CH_rural
  stat_compare_means(method = "wilcox.test",
                     comparisons =                
                       list(c("rural", "urban"), 
                            c("rural", "nat_terms"),
                            c("urban", "nat_terms"),
                            c("geoloc_nat", "urban"),
                            c("geoloc_nat", "rural"),
                            c("geoloc_nat", "nat_terms"),
                            c("geoloc_loc", "geoloc_nat"),
                            c("geoloc_loc", "urban"),
                            c("geoloc_loc", "rural"),
                            c("geoloc_loc", "nat_terms")),
                     na.rm = T,
                     label = "p.signif")

```



```{r}
heidi_SentiArt2  %>%
  # summarise(value = mean(value)) %>%
  ggplot(aes(x = emotion, y = value_scaled, fill = type)) +
  # ylim(-1,1) +
  # facet_wrap(~ type, scales = "free_y") +
  geom_boxplot(position = "dodge") +
  theme_minimal() +
  theme(axis.title.x = element_blank())



```


#### lmer

```{r}
sentiart_heidi_lmer <- lmer(value_scaled ~ type *emotion + 
                        (1|frequency) +
                        (1|doc_id),
     heidi_SentiArt2, REML = F)

tab_model(sentiart_heidi_lmer, show.se = T,
            show.ci = F,
            show.stat = T,
            emph.p = T,
            transform = NULL,
            string.pred = "Pred",
            string.stat = "z",
            string.se = "SE",
            show.icc = F) %>%
  return() %$% 
  knitr %>% 
  knitr::asis_output()
```

