---
title: "Test paper - sentiments grouped"
author: "Giulia Grisot"
date: "2020"
output:
  html_notebook: 
    theme: flatly
    fig_width: 8
    fig_height: 5
---

# Corpus preparation

```{r message=FALSE, warning=F}
library(tidyverse)
# library(harrypotter)
library(lme4)
library(lmerTest)
library(tidytext)
library(sjPlot)
library(ggplot2)
library(ggsci)
library(ggpubr)
library(sjstats)
library(knitr)

```


# frequency per entity type_grouped

```{r}

heidi_all_entities_long[,c("type_grouped","word")]  %>%
  group_by(type_grouped, word) %>%
  anti_join(heidi_names, by = "word") %>%  anti_join(stop_german, by = "word") %>% # delete stopwords
  count() %>% # summarize count per word per title
  arrange(desc(n)) %>% # highest frequency on top
  group_by(type_grouped)
# %>% # 
#   mutate(top = seq_along(word)) %>% # identify rank within group
#   filter(top <= 15) %>% # retain top 15 frequent words
#   # create barplot
#   ggplot(aes(x = -top, fill = type_grouped)) + 
#   geom_bar(aes(y = n), stat = 'identity', col = 'black') +
#   # make sure words are printed either in or next to bar
#   geom_text(aes(y = ifelse(n > max(n) / 2, max(n) / 50, n + max(n) / 50),
#                 label = word), size = fs/3, hjust = "left") +
#   theme_minimal() +
#   theme(legend.position = 'none', # get rid of legend
#         text = element_text(size = fs), # determine fs
#         axis.text.x = element_text(angle = 45, hjust = 1, size = fs/1.5), # rotate x text
#         axis.ticks.y = element_blank(), # remove y ticks
#         axis.text.y = element_blank()) + # remove y text
#   labs(y = "Word count", x = "", # add labels
#        title = "Most frequent words by type_grouped") +
#   facet_grid(. ~ type_grouped) + # separate plot for each book
#   coord_flip() + # flip axes
#   # scale_fill_hp(discrete = T, option = "Always")

```



# Sentiments by type_grouped

## BAWL 

### arousal

```{r}
heidi_BAWL %>%
  group_by(title, doc_id) %>%
  ggplot(aes(type_grouped, fill = type_grouped)) +
  geom_histogram(stat = "count", na.rm = T) +
  theme_minimal()

```


```{r}
heidi_BAWL %>%
  # summarise(value = mean(value)) %>%
  ggplot(aes(x = type_grouped, y = arousal, fill = type_grouped)) +
  # ylim(-2,2) +
  # facet_wrap(~ type_grouped, scales = "free_y") +
  geom_boxplot() +
  theme_minimal() +
  theme(axis.title.x = element_blank()) +
  ggtitle("BAWL", subtitle = "arousal") +
  stat_compare_means(method = "wilcox.test",
                     comparisons =                
                       list(c("NAT", "OTHER")),
                     na.rm = T,
                     label = "p.signif")


```

#### summary

```{r}

Rmisc::summarySE(heidi_BAWL, measurevar = "arousal",
          groupvars = c("type_grouped"),
          na.rm = TRUE,
          conf.interval = 0.95)

```

#### compare means

```{r}

compare_means(arousal ~ type_grouped, data = heidi_BAWL, method = "wilcox")

```

#### lmer

```{r}
BAWL_grouped_arousal_heidi_lmer <- lmer(arousal ~ type_grouped + 
                            (1|title) + 
                            (1|frequency),
                          heidi_BAWL, REML = F)

```


### valence (polarity)

```{r}
heidi_BAWL  %>%
  # summarise(value = mean(value)) %>%
  ggplot(aes(x = type_grouped, y = valence, fill = type_grouped)) +
  # ylim(-2,2) +
  # facet_wrap(~ type_grouped, scales = "free_y") +
  geom_boxplot() +
  theme_minimal() +
  theme(axis.title.x = element_blank()) +
  ggtitle("BAWL", subtitle = "valence") +
  stat_compare_means(method = "wilcox.test",
                     comparisons =                
                       list(c("NAT", "OTHER")),
                     na.rm = T,
                     label = "p.signif")

```

#### summary

```{r}

Rmisc::summarySE(heidi_BAWL, measurevar = "valence",
          groupvars = c("type_grouped"),
          na.rm = TRUE,
          conf.interval = 0.95)

```

#### compare means

```{r}

compare_means(valence ~ type_grouped, data = heidi_BAWL, method = "wilcox.test")


```

#### lmer

```{r}
BAWL_grouped_valence_heidi_lmer <- lmer(valence ~ type_grouped + 
                            (1|frequency) +
                            (1|title),
                          heidi_BAWL, REML = F)

```

### imageability

```{r}
heidi_BAWL  %>%
  # summarise(value = mean(value)) %>%
  ggplot(aes(x = type_grouped, y = imageability, fill = type_grouped)) +
  # ylim(-2,2) +
  # facet_wrap(~ type_grouped, scales = "free_y") +
  geom_boxplot() +
  theme_minimal() +
  theme(axis.title.x = element_blank()) +
  ggtitle("BAWL", subtitle = "imageability") +
  # if unified nat_term and CH_rural
  stat_compare_means(method = "wilcox.test",
                     comparisons =                
                       list(c("NAT", "OTHER")),
                     na.rm = T,
                     label = "p.signif")

```

#### summary

```{r}

Rmisc::summarySE(heidi_BAWL, measurevar = "imageability",
          groupvars = c("type_grouped"),
          na.rm = TRUE,
          conf.interval = 0.95)

```

#### compare means

```{r}

compare_means(imageability ~ type_grouped, data = heidi_BAWL, method = "wilcox.test")


```

#### lmer

```{r}
BAWL_grouped_imag_heidi_lmer <- lmer(imageability ~ type_grouped +
                         (1|frequency) +
                         (1|title),
                       heidi_BAWL, REML = F)


```


## SentiWS 

### polarity

```{r}
heidi_sentiWS %>%
  # summarise(value = mean(value)) %>%
  ggplot(aes(x = type_grouped, y = SentiWS_polarity, fill = type_grouped)) +
  # facet_wrap(~ type_grouped, scales = "free_y") +
  geom_boxplot() +
  theme_minimal() +
  theme(axis.title.x = element_blank()) +
  ggtitle("SentiWS", subtitle = "polarity") +
  stat_compare_means(method = "wilcox.test",
                     comparisons =                
                       list(c("NAT", "OTHER")),
                     na.rm = T,
                     label = "p.signif")

#   facet_grid(. ~ title)
```

#### summary

```{r}

Rmisc::summarySE(heidi_sentiWS, measurevar = "SentiWS_polarity",
          groupvars = c("type_grouped"),
          na.rm = TRUE,
          conf.interval = 0.95)

```

#### compare means

```{r}

compare_means(SentiWS_polarity ~ type_grouped, data = heidi_sentiWS, method = "wilcox.test")


```

#### lmer

```{r}
SentiWS_grouped_polarity_heidi_lmer <- lmer(SentiWS_polarity ~ type_grouped +
                                (1|frequency) +
                                (1|title),
                              heidi_sentiWS, REML = F)

```




## LANG 

### arousal

```{r}
heidi_LANG %>%
  # summarise(value = mean(value)) %>%
  ggplot(aes(x = type_grouped, y = arousal_mean, fill = type_grouped)) +
  # ylim(-2,2) +
  # facet_wrap(~ type_grouped, scales = "free_y") +
  geom_boxplot() +
    theme_minimal() +
  theme(axis.title.x = element_blank()) +
  ggtitle("LANG", subtitle = "arousal") +
  stat_compare_means(method = "wilcox.test",
                     comparisons =                
                       list(c("NAT", "OTHER")),
                     na.rm = T,
                     label = "p.signif")

```

#### summary

```{r}

Rmisc::summarySE(heidi_LANG, measurevar = "arousal_mean",
          groupvars = c("type_grouped"),
          na.rm = TRUE,
          conf.interval = 0.95)

```

#### compare means

```{r}

compare_means(arousal_mean ~ type_grouped, data = heidi_LANG, method = "wilcox.test")


```

#### lmer

```{r}
LANG_grouped_arousal_heidi_lmer <- lmer(arousal_mean ~ type_grouped + 
                            (1|frequency) +
                            (1|title),
                          heidi_LANG, REML = F)


# summary(LANG_arousal_heidi_lmer)

```

### valence

```{r}
heidi_LANG %>%
  # summarise(value = mean(value)) %>%
  ggplot(aes(x = type_grouped, y = valence_mean, fill = type_grouped)) +
  # ylim(-2,2) +
  # facet_wrap(~ type_grouped, scales = "free_y") +
  geom_boxplot() +
   theme_minimal() +
  theme(axis.title.x = element_blank()) +
  ggtitle("LANG", subtitle = "valence") +
    stat_compare_means(method = "wilcox.test",
                     comparisons =                
                       list(c("NAT", "OTHER")),
                     na.rm = T,
                     label = "p.signif")

```

#### summary

```{r}

Rmisc::summarySE(heidi_LANG, measurevar = "valence_mean",
          groupvars = c("type_grouped"),
          na.rm = TRUE,
          conf.interval = 0.95)

```

#### compare means

```{r}

compare_means(valence_mean ~ type_grouped, data = heidi_LANG, method = "wilcox.test")


```

#### lmer

```{r}
LANG_grouped_valence_heidi_lmer <- lmer(valence_mean ~ type_grouped + 
                            (1|frequency) +
                            (1|title),
                          heidi_LANG, REML = F)

```

### concreteness

```{r}
heidi_LANG %>%
  # summarise(value = mean(value)) %>%
  ggplot(aes(x = type_grouped, y = concreteness_mean, fill = type_grouped)) +
  # ylim(-2,2) +
  # facet_wrap(~ type_grouped, scales = "free_y") +
  geom_boxplot() +
    theme_minimal() +
  theme(axis.title.x = element_blank()) +
  ggtitle("LANG", subtitle = "concreteness") +
    stat_compare_means(method = "wilcox.test",
                     comparisons =                
                       list(c("NAT", "OTHER")),
                     na.rm = T,
                     label = "p.signif")

```

#### summary

```{r}

Rmisc::summarySE(heidi_LANG, measurevar = "concreteness_mean",
          groupvars = c("type_grouped"),
          na.rm = TRUE,
          conf.interval = 0.95)

```

#### compare means

```{r}

compare_means(concreteness_mean ~ type_grouped, data = heidi_LANG, method = "wilcox.test")


```

#### lmer

```{r}
LANG_grouped_concr_heidi_lmer <- lmer(concreteness_mean ~ type_grouped + 
                            (1|frequency) +
                            (1|title),
                          heidi_LANG, REML = F)

```

# discrete models

## Klinger

### emotions

#### absolute plot

```{r}

heidi_klinger %>%
  group_by(emotion, type_grouped) %>%
  filter(!is.na(emotion)) %>%
  summarize(count = n()) %>%
  ggplot(aes(x = emotion, y = count, fill = emotion)) +    
  geom_bar(stat = 'identity') +
  theme_minimal() +
  ggtitle("Klinger", subtitle = "absolute count") + 
  theme(legend.position = 'none', # get rid of legend
        axis.text.x = element_text(angle = 45, hjust = 1, size = fs/1.5)) + 
  
  facet_grid(. ~ type_grouped)

```

#### proportional plot

```{r}
heidi_klinger %>%
  group_by(type_grouped) %>%
  mutate(row_n_type_grouped = n()) %>%
  group_by(type_grouped, emotion) %>%
  summarise(emotion_count = n()/row_n_type_grouped) %>%
  group_by(emotion) %>%
  distinct() %>%
  filter(!is.na(emotion)) %>%
  ggplot(aes(x = emotion, y = emotion_count, fill = emotion)) +    
  geom_bar(stat = 'identity') +
  theme_minimal() +
  ggtitle("Klinger", subtitle = "proportional count") +
  theme(legend.position = 'none', # get rid of legend
        axis.text.x = element_text(angle = 45, hjust = 1, size = fs/1.5)) + 
  
  facet_grid(. ~ type_grouped)
```

```{r}
klinger_grouped_heidi_lmer <- lmer(emotion_count ~ type_grouped*emotion + 
                            (1|frequency) +
                            (1|title),
                          heidi_klinger, REML = F)


summary(klinger_grouped_heidi_lmer)
```

## Plutchnik

### emotions

#### absolute plot

```{r}

heidi_plutchik %>%
  group_by(emotion, type_grouped) %>%
  filter(!is.na(emotion)) %>%
  summarize(count = n()) %>%
  ggplot(aes(x = emotion, y = count, fill = emotion)) +    
  geom_bar(stat = 'identity') +
  theme_minimal() +
  ggtitle("Plutchik", subtitle = "absolute count") +
  theme(legend.position = 'none', # get rid of legend
        axis.text.x = element_text(angle = 45, hjust = 1, size = fs/1.5)) + 
  facet_grid(. ~ type_grouped)

```
#### proportional plot

```{r}
heidi_plutchik %>%
  group_by(type_grouped) %>%
  mutate(row_n_type_grouped = n()) %>%
  group_by(type_grouped, emotion) %>%
  summarise(emotion_count = n()/row_n_type_grouped) %>%
  group_by(emotion) %>%
  distinct() %>%
  filter(!is.na(emotion)) %>%
  ggplot(aes(x = emotion, y = emotion_count, fill = emotion)) +    
  geom_bar(stat = 'identity') +
  theme_minimal() +
  ggtitle("Plutchik", subtitle = "proportional count") +
  theme(legend.position = 'none', # get rid of legend
        axis.text.x = element_text(angle = 45, hjust = 1, size = fs/1.5)) + 
  facet_grid(. ~ type_grouped)

```

```{r}
plutchik_grouped_heidi_lmer <- lmer(emotion_count ~ type_grouped*emotion + 
                            (1|frequency) +
                            (1|title),
                          heidi_plutchik, REML = F)

summary(plutchik_grouped_heidi_lmer)
```


## Sentiart

#### summary

```{r}

Rmisc::summarySE(heidi_SentiArt2,
                 measurevar = "value_scaled",
          groupvars = c("type_grouped", "emotion"),
          na.rm = TRUE,
          conf.interval = 0.95)

```

#### compare means

```{r}
compare_means(value_scaled ~ type_grouped, data = heidi_SentiArt2, method = "wilcox.test", group.by = "emotion")

```

#### absolute plot

```{r}
heidi_SentiArt2 %>%
  ggplot(aes(x = emotion, y = value_scaled, fill = emotion)) +    
  geom_bar(stat = 'identity') +
  theme_minimal() +
  ggtitle("SentiArt", subtitle = "absolute count") +
  theme(legend.position = 'none', # get rid of legend
        axis.text.x = element_text(angle = 45, hjust = 1, size = fs/1.5)) + 
  facet_grid(. ~ type_grouped)
```


#### proportional plot

```{r}

heidi_SentiArt2 %>%
  group_by(type_grouped) %>%
  mutate(row_n_type_grouped = n()) %>%
  group_by(type_grouped, emotion) %>%
  summarise(emotion_value = value_scaled/row_n_type_grouped) %>%
  group_by(emotion) %>%
  distinct() %>%
  filter(!is.na(emotion)) %>%
  ggplot(aes(x = emotion, y = emotion_value, fill = emotion)) +    
  geom_bar(stat = 'identity') +
  theme_minimal() +
  ggtitle("SentiArt") +
  theme(legend.position = 'none', # get rid of legend
        axis.text.x = element_text(angle = 45, hjust = 1, size = fs/1.5)) + 
  facet_grid(. ~ type_grouped)


```
## single emotions comparisons

### fear

```{r}
heidi_SentiArt2 %>%
  filter(emotion == "fear_z") %>%
  ggplot(aes(x = type_grouped, y = value_scaled, fill = type_grouped)) +
  # ylim(-2,2) +
  # facet_wrap(~ type_grouped, scales = "free_y") +
  geom_boxplot() +
  theme_minimal() +
  theme(axis.title.x = element_blank()) +
  ggtitle("sentiArt", subtitle = "fear") +
  # if unified nat_term and CH_rural
  stat_compare_means(method = "wilcox.test",
                     comparisons =                
                       list(c("NAT", "OTHER")),
                     na.rm = T,
                     label = "p.signif")

```



### disgust


```{r}
heidi_SentiArt2 %>%
  filter(emotion == "disg_z") %>%
  ggplot(aes(x = type_grouped, y = value_scaled, fill = type_grouped)) +
  # ylim(-2,2) +
  # facet_wrap(~ type_grouped, scales = "free_y") +
  geom_boxplot() +
  theme_minimal() +
  theme(axis.title.x = element_blank()) +
  ggtitle("sentiArt", subtitle = "disgust") +
  # if unified nat_term and CH_rural
  stat_compare_means(method = "wilcox.test",
                     comparisons =                
                       list(c("NAT", "OTHER")),
                     na.rm = T,
                     label = "p.signif")

```

### happyness


```{r}
heidi_SentiArt2 %>%
  filter(emotion == "hap_z") %>%
  ggplot(aes(x = type_grouped, y = value_scaled, fill = type_grouped)) +
  # ylim(-2,2) +
  # facet_wrap(~ type_grouped, scales = "free_y") +
  geom_boxplot() +
  theme_minimal() +
  theme(axis.title.x = element_blank()) +
  ggtitle("sentiArt", subtitle = "happiness") +
  # if unified nat_term and CH_rural
  stat_compare_means(method = "wilcox.test",
                     comparisons =                
                       list(c("NAT", "OTHER")),
                     na.rm = T,
                     label = "p.signif")

```


### sadness

```{r}
heidi_SentiArt2 %>%
  filter(emotion == "sad_z") %>%
  ggplot(aes(x = type_grouped, y = value_scaled, fill = type_grouped)) +
  # ylim(-2,2) +
  # facet_wrap(~ type_grouped, scales = "free_y") +
  geom_boxplot() +
  theme_minimal() +
  theme(axis.title.x = element_blank()) +
  ggtitle("sentiArt", subtitle = "sadness") +
  # if unified nat_term and CH_rural
  stat_compare_means(method = "wilcox.test",
                     comparisons =                
                       list(c("NAT", "OTHER")),
                     na.rm = T,
                     label = "p.signif")

```


### surprise


```{r}
heidi_SentiArt2 %>%
  filter(emotion == "surp_z") %>%
  ggplot(aes(x = type_grouped, y = value_scaled, fill = type_grouped)) +
  # ylim(-2,2) +
  # facet_wrap(~ type_grouped, scales = "free_y") +
  geom_boxplot() +
  theme_minimal() +
  theme(axis.title.x = element_blank()) +
  ggtitle("sentiArt", subtitle = "surprise") +
  # if unified nat_term and CH_rural
  stat_compare_means(method = "wilcox.test",
                     comparisons =                
                       list(c("NAT", "OTHER")),
                     na.rm = T,
                     label = "p.signif")

```


### anger

```{r}

heidi_SentiArt2 %>%
  filter(emotion == "ang_z") %>%
  ggplot(aes(x = type_grouped, y = value_scaled, fill = type_grouped)) +
  # ylim(-2,2) +
  # facet_wrap(~ type_grouped, scales = "free_y") +
  geom_boxplot() +
  theme_minimal() +
  theme(axis.title.x = element_blank()) +
  ggtitle("sentiArt", subtitle = "anger") +
  # if unified nat_term and CH_rural
  stat_compare_means(method = "wilcox.test",
                     comparisons =                
                       list(c("NAT", "OTHER")),
                     na.rm = T,
                     label = "p.signif")

```



```{r}
heidi_SentiArt2  %>%
  # summarise(value = mean(value)) %>%
  ggplot(aes(x = emotion, y = value_scaled, fill = type_grouped)) +
  # ylim(-1,1) +
  # facet_wrap(~ type_grouped, scales = "free_y") +
  geom_boxplot(position = "dodge") +
  theme_minimal() +
  theme(axis.title.x = element_blank())



```





### lmer

```{r}
sentiart_grouped_heidi_lmer <- lmer(value_scaled ~ type_grouped*emotion +
                                (1|frequency) +
                                (1|doc_id),
                              heidi_SentiArt2, REML = F)

```


# mixed models comparison

```{r}
tab_model(BAWL_grouped_arousal_heidi_lmer,
  BAWL_grouped_valence_heidi_lmer,
  BAWL_grouped_imag_heidi_lmer,
            show.se = T,
          show.ci = F,
          show.stat = T,
          emph.p = T,
          transform = NULL,
          string.pred = "Pred",
          string.stat = "z",
          string.se = "SE",
          show.icc = F) %>% 
    return() %$% 
    knitr::knitr %>% 
    knitr::asis_output()
```


LANG_grouped_arousal_heidi_lmer,
  LANG_grouped_valence_heidi_lmer,
  LANG_grouped_concr_heidi_lmer,
  SentiWS_grouped_polarity_heidi_lmer,
  
```{r}

tab_model(klinger_grouped_heidi_lmer,
            show.se = T,
          show.ci = F,
          show.stat = T,
          emph.p = T,
          transform = NULL,
          string.pred = "Pred",
          string.stat = "z",
          string.se = "SE",
          show.icc = F) %>% 
    return() %$% 
    knitr %>% 
    knitr::asis_output()
```


```{r}
tab_model(plutchik_grouped_heidi_lmer,
            show.se = T,
          show.ci = F,
          show.stat = T,
          emph.p = T,
          transform = NULL,
          string.pred = "Pred",
          string.stat = "z",
          string.se = "SE",
          show.icc = F) %>% 
    return() %$% 
    knitr::knitr %>% 
    knitr::asis_output()
  
```


```{r}
tab_model(sentiart_grouped_heidi_lmer,
            show.se = T,
          show.ci = F,
          show.stat = T,
          emph.p = T,
          transform = NULL,
          string.pred = "Pred",
          string.stat = "z",
          string.se = "SE",
          show.icc = F) %>% 
    return() %$% 
    knitr %>% 
    knitr::asis_output()
```

