---
title: "Heidi - sentiments"
author: "Giulia Grisot"
date: "2020"
output:
  html_notebook: 
    theme: flatly
    fig_width: 8
    fig_height: 5
---

# Corpus preparation

```{r message=FALSE, warning=F}
library(tidyverse)
# library(harrypotter)
library(lme4)
library(lmerTest)
library(tidytext)
library(sjPlot)
library(ggplot2)
library(ggsci)
library(ggpubr)
library(wesanderson)

```

# make corpus by word 

```{r}
 corpus_all_entities_long <- corpus_all_entities %>%
  unnest_tokens(word, text, to_lower = F) %>%
  group_by(doc_id) %>%
  dplyr::mutate(word_id = row_number()) %>%
  group_by(word) %>%
  dplyr::mutate(freq = n()) %>%
  ungroup()
# %>%
#   mutate(type = ifelse(type == "CH_urban", "urban", "rural"))
# mutate(urban_rural = ifelse(type == "CH_city_village" | type == "CH_building_spots" | type == "CH_country_regions" | type == "CH_roads", "urban", "rural"))

corpus_all_entities_long$type <- as.factor(corpus_all_entities_long$type)
corpus_all_entities_long$title <- as.factor(corpus_all_entities_long$title)

```


```{r}
theme_set(theme_light()) # set default ggplot theme to light
fs = 10 # default plot font size
```

```{r}
all_entities_long %>%
  ggplot(aes(type)) +
  geom_histogram(stat = "count")

```

```{r}
all_entities_long %>%
  ggplot(aes(type2)) +
  geom_histogram(stat = "count")
```
```{r}
corpus_all_entities %>%
  group_by(title, doc_id) %>%
  ggplot(aes(type)) +
  geom_histogram(stat = "count")
```

? since rural terms could be considered part of the natural sphere, we could unify nat term and rural labels

```{r}
corpus_all_entities_long$type[corpus_all_entities_long$type == "nat_terms"] <- "CH_rural"

```


# Freq per book

```{r}
corpus_all_entities_long <- corpus_all_entities_long %>%
  anti_join(stop_german, by = "word") # delete stopwords

corpus_all_entities_long  %>%
  dplyr::group_by(title, word) %>%
  dplyr::summarise(count = count(n)) # summarize count per word per title
  arrange(desc(word_count))
  
  # highest freq on top# %>% # 
#   mutate(top = seq_along(word)) %>% # identify rank within group
#   filter(top <= 15) %>% # retain top 15 frequent words
#   # create barplot
#   ggplot(aes(x = -top, fill = title)) + 
#   geom_bar(aes(y = n), stat = 'identity', col = 'black') +
#   # make sure words are printed either in or next to bar
#   geom_text(aes(y = ifelse(n > max(n) / 2, max(n) / 50, n + max(n) / 50),
#                 label = word), size = fs/3, hjust = "left") +
#   theme_sjplot2() +
#   theme(legend.position = 'none', # get rid of legend
#         text = element_text(size = fs), # determine fs
#         axis.text.x = element_text(angle = 45, hjust = 1, size = fs/1.5), # rotate x text
#         axis.ticks.y = element_blank(), # remove y ticks
#         axis.text.y = element_blank()) + # remove y text
#   labs(y = "Word count", x = "", # add labels
#        title = "Most frequent words by book") +
#   facet_grid(. ~ title) + # separate plot for each book
#   coord_flip() + # flip axes
#   # scale_fill_hp(discrete = T, option = "Always")
#   scale_fill_simpsons()

```

# Freq per entity type

```{r}

corpus_all_entities_long[,c("type","word")]  %>%
  group_by(type, word) %>%
  anti_join(stop_german, by = "word") %>% # delete stopwords
  count() %>% # summarize count per word per title
  arrange(desc(n)) %>% # highest freq on top
  group_by(type)
# %>% # 
#   mutate(top = seq_along(word)) %>% # identify rank within group
#   filter(top <= 15) %>% # retain top 15 frequent words
#   # create barplot
#   ggplot(aes(x = -top, fill = type)) + 
#   geom_bar(aes(y = n), stat = 'identity', col = 'black') +
#   # make sure words are printed either in or next to bar
#   geom_text(aes(y = ifelse(n > max(n) / 2, max(n) / 50, n + max(n) / 50),
#                 label = word), size = fs/3, hjust = "left") +
#   theme_sjplot2() +
#   theme(legend.position = 'none', # get rid of legend
#         text = element_text(size = fs), # determine fs
#         axis.text.x = element_text(angle = 45, hjust = 1, size = fs/1.5), # rotate x text
#         axis.ticks.y = element_blank(), # remove y ticks
#         axis.text.y = element_blank()) + # remove y text
#   labs(y = "Word count", x = "", # add labels
#        title = "Most frequent words by type") +
#   facet_grid(. ~ type) + # separate plot for each book
#   coord_flip() + # flip axes
#   # scale_fill_hp(discrete = T, option = "Always")
#   scale_fill_simpsons()

```



# Sentiments by type

## BAWL 

### arousal

```{r}

corpus_BAWL <- corpus_all_entities_long %>%
  anti_join(stop_german, by = "word") %>%
  left_join(BAWL_emotions, by = "word")

```

if we wanted to ahve a "sentiment" per passage, i.e per doc_id, we should sum uo the value of sentiment grouping it back 
```{r}
corpus_BAWL <- corpus_BAWL %>%
  dplyr::group_by(type, doc_id, pattern) 
  summarise(arousal = sum(arousal, na.rm = T), valence = sum(valence, na.rm = T), imageability = sum(imageability, na.rm = T), freq = mean(freq, na.rm = T))
```


```{r}
corpus_BAWL %>%
  # summarise(value = mean(value)) %>%
  ggplot(aes(x = type, y = arousal, fill = type)) +
  # ylim(-2,2) +
  # facet_wrap(~ type, scales = "free_y") +
  geom_boxplot() +
  theme_sjplot2() +
  theme(legend.position = 'none', # get rid of legend
        axis.text.x = element_text(angle = 45, hjust = 1, size = fs/1.5)) + 
  scale_fill_simpsons() +
  # if unified nat_term and CH_rural
    ggpubr::stat_compare_means(method = "wilcox.test",
                             comparisons = list(c("CH_rural", "CH_urban")),
                             na.rm = T,
                             label = "p.signif")

```

#### summary

```{r}

Rmisc::summarySE(corpus_BAWL, measurevar = "arousal",
          groupvars = c("type"),
          na.rm = TRUE,
          conf.interval = 0.95)

```

#### compare means

```{r}

compare_means(arousal ~ type, data = corpus_BAWL, method = "wilcox")

```

#### lmer

```{r}
BAWL_arousal_lmer <- lmer(arousal ~ type + 
                            (1|title) + 
                            (1|freq),
                          corpus_BAWL, REML = F)

tab_model(BAWL_arousal_lmer, 
          show.se = T,
            show.ci = F,
            show.stat = T,
            emph.p = T,
            transform = NULL,
            string.pred = "Pred",
            string.stat = "z",
            string.se = "SE",
            show.icc = F) %>%
  return() %$% 
  knitr %>% 
  knitr::asis_output()

```

```{r}
anova(BAWL_arousal_lmer)
```


### valence (polarity)

```{r}
corpus_BAWL  %>%
  # summarise(value = mean(value)) %>%
  ggplot(aes(x = type, y = valence, fill = type)) +
  # ylim(-2,2) +
  # facet_wrap(~ type, scales = "free_y") +
  geom_boxplot() +
  theme_sjplot2() +
  theme(legend.position = 'none', # get rid of legend
        axis.text.x = element_text(angle = 45, hjust = 1, size = fs/1.5)) + 
  scale_fill_simpsons() +
  # if unified nat_term and CH_rural
    ggpubr::stat_compare_means(method = "wilcox.test",
                             comparisons = list(c("CH_rural", "CH_urban")),
                             na.rm = T,
                             label = "p.signif")
```

#### summary

```{r}

Rmisc::summarySE(corpus_BAWL, measurevar = "valence",
          groupvars = c("type"),
          na.rm = TRUE,
          conf.interval = 0.95)

```

#### compare means

```{r}

compare_means(valence ~ type, data = corpus_BAWL, method = "wilcox.test")


```

#### lmer

```{r}
BAWL_valence_lmer <- lmer(valence ~ type + 
                            (1|freq) +
                            (1|title),
                          corpus_BAWL, REML = F)

tab_model(BAWL_valence_lmer, show.se = T,
            show.ci = F,
            show.stat = T,
            emph.p = T,
            transform = NULL,
            string.pred = "Pred",
            string.stat = "z",
            string.se = "SE",
            show.icc = F) %>%
  return() %$% 
  knitr %>% 
  knitr::asis_output()
```

```{r}
anova(BAWL_valence_lmer)

```

### imageability

```{r}
corpus_BAWL  %>%
  # summarise(value = mean(value)) %>%
  ggplot(aes(x = type, y = imageability, fill = type)) +
  # ylim(-2,2) +
  # facet_wrap(~ type, scales = "free_y") +
  geom_boxplot() +
  theme_sjplot2() +
  theme(legend.position = 'none', # get rid of legend
        axis.text.x = element_text(angle = 45, hjust = 1, size = fs/1.5)) + 
  scale_fill_simpsons()+
  # if unified nat_term and CH_rural
    ggpubr::stat_compare_means(method = "wilcox.test",
                             comparisons = list(c("CH_rural", "CH_urban")),
                             na.rm = T,
                             label = "p.signif")

```

#### summary

```{r}

Rmisc::summarySE(corpus_BAWL, measurevar = "imageability",
          groupvars = c("type"),
          na.rm = TRUE,
          conf.interval = 0.95)

```

#### compare means

```{r}

compare_means(imageability ~ type, data = corpus_BAWL, method = "wilcox.test")


```

#### lmer

```{r}
BAWL_imag_lmer <- lmer(imageability ~ type +
                         (1|freq) +
                         (1|title),
                       corpus_BAWL, REML = F)

tab_model(BAWL_imag_lmer, show.se = T,
            show.ci = F,
            show.stat = T,
            emph.p = T,
            transform = NULL,
            string.pred = "Pred",
            string.stat = "z",
            string.se = "SE",
            show.icc = F) %>%
  return() %$% 
  knitr %>% 
  knitr::asis_output()

```


```{r}

anova(BAWL_imag_lmer)

# rstatix::anova_test(corpus_BAWL, formula = imageability ~ type)
```

## SentiWS 

```{r}

corpus_sentiWS <- corpus_all_entities_long %>%
  anti_join(stop_german, by = "word") %>%
  left_join(sentiWS_long, by = "word")

```

```{r}
lowest_negative_value = min(corpus_sentiWS$SentiWS_polarity, na.rm = T)

corpus_sentiWS <- corpus_sentiWS %>%
  mutate(SentiWS_polarity = SentiWS_polarity - lowest_negative_value)

corpus_sentiWS <- corpus_sentiWS %>%
  dplyr::group_by(type, author, title, doc_id, pattern) %>%  
  summarise(SentiWS_polarity = sum(SentiWS_polarity, na.rm = T), freq = mean(freq, na.rm = T))

```

### polarity

```{r}
corpus_sentiWS %>%
  # summarise(value = mean(value)) %>%
  ggplot(aes(x = type, y = SentiWS_polarity, fill = type)) +
  ylim(0,200) +
  # facet_wrap(~ type, scales = "free_y") +
  geom_boxplot() +
  theme_sjplot2() +
  theme(legend.position = 'none', # get rid of legend
        axis.text.x = element_text(angle = 45, hjust = 1, size = fs/1.5)) +
  scale_fill_simpsons() +
  # if unified nat_term and CH_rural
    ggpubr::stat_compare_means(method = "wilcox.test",
                             comparisons = list(c("CH_rural", "CH_urban")),
                             na.rm = T,
                             label = "p.signif")
# +
#   facet_grid(. ~ title)
```

#### summary

```{r}

Rmisc::summarySE(corpus_sentiWS, measurevar = "SentiWS_polarity",
          groupvars = c("type"),
          na.rm = TRUE,
          conf.interval = 0.95)

```

#### compare means

```{r}

compare_means(SentiWS_polarity ~ type, data = corpus_sentiWS, method = "wilcox.test")


```

#### lmer

```{r}
SentiWS_polarity_lmer <- lmer(SentiWS_polarity ~ type +
                                (1|freq) +
                                (1|title),
                              corpus_sentiWS, REML = F)

tab_model(SentiWS_polarity_lmer, show.se = T,
            show.ci = F,
            show.stat = T,
            emph.p = T,
            transform = NULL,
            string.pred = "Pred",
            string.stat = "z",
            string.se = "SE",
            show.icc = F) %>%
  return() %$% 
  knitr %>% 
  knitr::asis_output()

```

```{r}
anova(SentiWS_polarity_lmer)

```

## LANG 

```{r}

corpus_LANG <- corpus_all_entities_long %>%
  anti_join(stop_german, by = "word") %>%
 left_join(LANG_processed, by = "word")

# ks.test(corpus_LANG$arousal_mean, "pnorm", mean=mean(corpus_LANG$arousal_mean), sd=sd(corpus_LANG$arousal_mean))
# ks.test(corpus_LANG$valence_mean, "pnorm", mean=mean(corpus_LANG$valence_mean), sd=sd(corpus_LANG$valence_mean))
# 

# ggplot(corpus_LANG, aes(arousal_mean)) +
#   geom_histogram()
# ggplot(corpus_LANG, aes(valence_mean)) +
#   geom_histogram()

```

```{r}
corpus_LANG <- corpus_LANG %>%
  dplyr::group_by(type, author, title, doc_id, pattern) %>%
  summarise(arousal_mean = sum(arousal_mean, na.rm = T), valence_mean = sum(valence_mean, na.rm = T), concreteness_mean = sum(concreteness_mean, na.rm = T), freq = mean(freq, na.rm = T))
```

### arousal

```{r}
corpus_LANG %>%
  # summarise(value = mean(value)) %>%
  ggplot(aes(x = type, y = arousal_mean, fill = type)) +
  # ylim(-2,2) +
  # facet_wrap(~ type, scales = "free_y") +
  geom_boxplot() +
  theme_sjplot2() +
  theme(legend.position = 'none', # get rid of legend
        axis.text.x = element_text(angle = 45, hjust = 1, size = fs/1.5)) + 
  scale_fill_simpsons()+
  # if unified nat_term and CH_rural
    ggpubr::stat_compare_means(method = "wilcox.test",
                             comparisons = list(c("CH_rural", "CH_urban")),
                             na.rm = T,
                             label = "p.signif")

```

#### summary

```{r}

Rmisc::summarySE(corpus_LANG, measurevar = "arousal_mean",
          groupvars = c("type"),
          na.rm = TRUE,
          conf.interval = 0.95)

```

#### compare means

```{r}

compare_means(arousal_mean ~ type, data = corpus_LANG, method = "wilcox.test")


```

#### lmer

```{r}
LANG_arousal_lmer <- lmer(arousal_mean ~ type + 
                            (1|freq) +
                            (1|title),
                          corpus_LANG, REML = F)


tab_model(LANG_arousal_lmer, show.se = T,
            show.ci = F,
            show.stat = T,
            emph.p = T,
            transform = NULL,
            string.pred = "Pred",
            string.stat = "z",
            string.se = "SE",
            show.icc = F) %>%
  return() %$% 
  knitr %>% 
  knitr::asis_output()

# summary(LANG_arousal_lmer)

```

```{r}
anova(LANG_arousal_lmer)
```



### valence

```{r}
corpus_LANG %>%
  # summarise(value = mean(value)) %>%
  ggplot(aes(x = type, y = valence_mean, fill = type)) +
  # ylim(-2,2) +
  # facet_wrap(~ type, scales = "free_y") +
  geom_boxplot() +
  theme_sjplot2() +
  theme(legend.position = 'none', # get rid of legend
        axis.text.x = element_text(angle = 45, hjust = 1, size = fs/1.5)) + 
  scale_fill_simpsons() +
  # if unified nat_term and CH_rural
    ggpubr::stat_compare_means(method = "wilcox.test",
                             comparisons = list(c("CH_rural", "CH_urban")),
                             na.rm = T,
                             label = "p.signif")
```

#### summary

```{r}

Rmisc::summarySE(corpus_LANG, measurevar = "valence_mean",
          groupvars = c("type"),
          na.rm = TRUE,
          conf.interval = 0.95)

```

#### compare means

```{r}

compare_means(valence_mean ~ type, data = corpus_LANG, method = "wilcox.test")


```

#### lmer

```{r}
LANG_valence_lmer <- lmer(valence_mean ~ type + 
                            (1|freq) +
                            (1|title),
                          corpus_LANG, REML = F)

tab_model(LANG_valence_lmer, show.se = T,
            show.ci = F,
            show.stat = T,
            emph.p = T,
            transform = NULL,
            string.pred = "Pred",
            string.stat = "z",
            string.se = "SE",
            show.icc = F) %>%
  return() %$% 
  knitr %>% 
  knitr::asis_output()

```

```{r}
anova(LANG_valence_lmer)
```

### concreteness

```{r}
corpus_LANG %>%
  # summarise(value = mean(value)) %>%
  ggplot(aes(x = type, y = concreteness_mean, fill = type)) +
  # ylim(-2,2) +
  # facet_wrap(~ type, scales = "free_y") +
  geom_boxplot() +
  theme_sjplot2() +
  theme(legend.position = 'none', # get rid of legend
        axis.text.x = element_text(angle = 45, hjust = 1, size = fs/1.5)) + 
  scale_fill_simpsons() +
  # if unified nat_term and CH_rural
    ggpubr::stat_compare_means(method = "wilcox.test",
                             comparisons = list(c("CH_rural", "CH_urban")),
                             na.rm = T,
                             label = "p.signif")
```

#### summary

```{r}

Rmisc::summarySE(corpus_LANG, measurevar = "concreteness_mean",
          groupvars = c("type"),
          na.rm = TRUE,
          conf.interval = 0.95)

```

#### compare means

```{r}

compare_means(concreteness_mean ~ type, data = corpus_LANG, method = "wilcox.test")


```

#### lmer

```{r}
LANG_concreteness_lmer <- lmer(concreteness_mean ~ type + 
                            (1|freq) +
                            (1|title),
                          corpus_LANG, REML = F)

tab_model(LANG_concreteness_lmer, show.se = T,
            show.ci = F,
            show.stat = T,
            emph.p = T,
            transform = NULL,
            string.pred = "Pred",
            string.stat = "z",
            string.se = "SE",
            show.icc = F) %>%
  return() %$% 
  knitr %>% 
  knitr::asis_output()

```

```{r}
anova(LANG_concreteness_lmer)
```


## Klinger

```{r}
corpus_klinger <- corpus_all_entities_long %>%
  anti_join(stop_german, by = "word") %>%
  left_join(klinger, by = "word")

corpus_klinger$emotion <- as.factor(corpus_klinger$emotion)
```


```{r}
# corpus_LANG <- corpus_LANG %>%
#   dplyr::group_by(type, author, title, doc_id, pattern) %>%
#   summarise(arousal_mean = sum(arousal_mean, na.rm = T), valence_mean = sum(valence_mean, na.rm = T), concreteness_mean = sum(concreteness_mean, na.rm = T), freq = mean(freq, na.rm = T))
```

### emotions

#### absolute plot

```{r}

corpus_klinger %>%
  group_by(title, emotion, type) %>%
  filter(!is.na(emotion)) %>%
  summarize(count = n()) %>%
  ggplot(aes(x = emotion, y = count, fill = emotion)) +    
  geom_bar(stat = 'identity') +
  theme_sjplot2() +
  theme(legend.position = 'none', # get rid of legend
        axis.text.x = element_text(angle = 45, hjust = 1, size = fs/1.5)) + 
  scale_fill_simpsons() +
  facet_grid(. ~ type)

```

#### proportional plot

```{r}
corpus_klinger %>%
  group_by(type) %>%
  mutate(row_n_type = n()) %>%
  group_by(type, emotion) %>%
  summarise(emotion_count = n()/row_n_type) %>%
  group_by(emotion) %>%
  distinct() %>%
  filter(!is.na(emotion)) %>%
  ggplot(aes(x = emotion, y = emotion_count, fill = emotion)) +    
  geom_bar(stat = 'identity') +
  theme_sjplot2() +
  theme(legend.position = 'none', # get rid of legend
        axis.text.x = element_text(angle = 45, hjust = 1, size = fs/1.5)) + 
  scale_fill_simpsons() +
  facet_grid(. ~ type)
```


### Words carrying strongest emotions Klinger

```{r fig.height=7, fig.width=10}

corpus_klinger %>% 
  group_by(word, emotion, type) %>%
  count() %>% # summarize count per word per sentiment
  group_by(emotion) %>%
  arrange(emotion, desc(n)) %>% # most frequent on top
  mutate(top = seq_along(word)) %>% # identify rank within group
  filter(top <= 15) %>% # keep top 15 frequent words
  ggplot(aes(x = -top, fill = factor(emotion))) + 
  # create barplot
  geom_bar(aes(y = n), stat = 'identity', col = 'black') +
  # make sure words are printed either in or next to bar
  geom_text(aes(y = ifelse(n > max(n) / 2, max(n) / 50, n + max(n) / 50),
                label = word), size = fs/3, hjust = "left") +
  theme_sjplot2() +
  scale_fill_jco() +
  theme(legend.position = 'none', # remove legend
        text = element_text(size = fs), # determine fs
        axis.text.x = element_text(angle = 45, hjust = 1), # rotate x text
        axis.ticks.y = element_blank(), # remove y ticks
        axis.text.y = element_blank()) + # remove y text
  labs(y = "Word count", x = "", # add manual labels
       title = "Words carrying strongest emotions") +
  facet_grid(. ~ emotion, scales = "free") + # separate plot for each sentiment
  coord_flip() # flip axes


```


```{r}
summary(corpus_klinger)
```

```{r}
corpus_klinger %>%
  filter(!is.na(emotion)) %>%
  ggplot(aes(emotion, fill = type)) +
  geom_bar(stat = "count", position = "dodge", show.legend = T) +
  theme_sjplot2() +
  scale_fill_simpsons() +
  theme(legend.position = "bottom",
        text = element_text(size = fs), # determine fs
        axis.text.x = element_text(angle = 45, hjust = 1) # rotate x text
        )
```



```{r}

ggplot(corpus_klinger, aes(emotion, fill = type)) +
  geom_bar(stat = "count", position = "fill") +
  theme_sjplot2() +
  scale_fill_simpsons() +
  theme(legend.position = "bottom",
        text = element_text(size = fs), # determine fs
        axis.text.x = element_text(angle = 45, hjust = 1) # rotate x text
        )


```


```{r}
corpus_klinger %>%
  filter(!is.na(emotion)) %>%
  ggplot(aes(emotion, fill = type)) +
  geom_histogram(stat = "count", position = "dodge") +
  facet_wrap(. ~ title, scales = "free_y")  +
  theme_sjplot2() +
  scale_fill_simpsons() +
  theme(legend.position = "bottom",
        text = element_text(size = fs), # determine fs
        axis.text.x = element_text(angle = 45, hjust = 1) # rotate x text
        )

```

## Plutchnik

```{r}
corpus_plutchik <- corpus_all_entities_long %>%
  anti_join(stop_german, by = "word") %>%
  left_join(plutchik, by = "word")

```


### emotions

#### absolute plot

```{r}

corpus_plutchik %>%
  group_by(title, emotion, type) %>%
  filter(!is.na(emotion)) %>%
  summarize(count = n()) %>%
  ggplot(aes(x = emotion, y = count, fill = emotion)) +    
  geom_bar(stat = 'identity') +
  theme_sjplot2() +
  theme(legend.position = 'none', # get rid of legend
        axis.text.x = element_text(angle = 45, hjust = 1, size = fs/1.5)) + 
  scale_fill_simpsons() +
  facet_grid(. ~ type)

```
#### proportional plot

```{r}
corpus_plutchik %>%
  group_by(type) %>%
  mutate(row_n_type = n()) %>%
  group_by(type, emotion) %>%
  summarise(emotion_count = n()/row_n_type) %>%
  group_by(emotion) %>%
  distinct() %>%
  filter(!is.na(emotion)) %>%
  ggplot(aes(x = emotion, y = emotion_count, fill = emotion)) +    
  geom_bar(stat = 'identity') +
  theme_sjplot2() +
  theme(legend.position = 'none', # get rid of legend
        axis.text.x = element_text(angle = 45, hjust = 1, size = fs/1.5)) + 
  scale_fill_simpsons() +
  facet_grid(. ~ type)
```

#### summary

```{r}
# 
# corpus_plutchik %>%
#   dplyr::group_by(emotion, type) %>%
#   dplyr::summarise(count = count(row_number(word)))
```



### Words carrying strongest emotions Plutchnik

```{r fig.height=7, fig.width=10}

corpus_plutchik %>% 
  group_by(word, emotion) %>%
  count() %>% # summarize count per word per sentiment
  group_by(emotion) %>%
  arrange(emotion, desc(n)) %>% # most frequent on top
  mutate(top = seq_along(word)) %>% # identify rank within group
  filter(top <= 15) %>% # keep top 15 frequent words
  ggplot(aes(x = -top, fill = factor(emotion))) + 
  # create barplot
  geom_bar(aes(y = n), stat = 'identity', col = 'black') +
  # make sure words are printed either in or next to bar
  geom_text(aes(y = ifelse(n > max(n) / 2, max(n) / 50, n + max(n) / 50),
                label = word), size = fs/3, hjust = "left") +
  theme_sjplot2() +
  scale_fill_jco() +
  theme(legend.position = 'none', # remove legend
        text = element_text(size = fs), # determine fs
        axis.text.x = element_text(angle = 45, hjust = 1), # rotate x text
        axis.ticks.y = element_blank(), # remove y ticks
        axis.text.y = element_blank()) + # remove y text
  labs(y = "Word count", x = "", # add manual labels
       title = "Words carrying strongest emotions") +
  facet_grid(. ~ emotion, scales = "free") + # separate plot for each sentiment
  coord_flip() # flip axes


```

```{r}
summary(corpus_plutchik)
```

```{r}
corpus_plutchik %>%
  filter(!is.na(emotion)) %>%
  ggplot(aes(emotion, fill = type)) +
  geom_bar(stat = "count", position = "dodge", show.legend = T) +
  theme_sjplot2() +
  scale_fill_simpsons() +
  theme(legend.position = "bottom",
        text = element_text(size = fs), # determine fs
        axis.text.x = element_text(angle = 45, hjust = 1) # rotate x text
        )
```

```{r}

# corpus_plutchik <- corpus_plutchik %>%
#   group_by(type, emotion) %>%
#   mutate(emotion_proportion = n()) %>%
#   ungroup()
# 
# corpus_plutchik <- corpus_plutchik %>%
#   group_by(type) %>%
#   mutate(emotion_proportion2 = n()) %>%
#   ungroup()
# 
# corpus_plutchik <- corpus_plutchik %>%
#   mutate(emotion_proportion = emotion_proportion/emotion_proportion2*100)
# 
# corpus_plutchik$emotion_proportion2 <- NULL




ggplot(corpus_plutchik, aes(emotion, fill = type)) +
  geom_bar(stat = "count", position = "fill") +
  theme_sjplot2() +
  scale_fill_simpsons() +
  theme(legend.position = "bottom",
        text = element_text(size = fs), # determine fs
        axis.text.x = element_text(angle = 45, hjust = 1) # rotate x text
        )


```


```{r}
corpus_plutchik %>%
  filter(!is.na(emotion)) %>%
  ggplot(aes(emotion, fill = type)) +
  geom_histogram(stat = "count", position = "dodge") +
  facet_wrap(. ~ title, scales = "free_y")  +
  theme_sjplot2() +
  scale_fill_simpsons() +
  theme(legend.position = "bottom",
        text = element_text(size = fs), # determine fs
        axis.text.x = element_text(angle = 45, hjust = 1) # rotate x text
        )

```

## Sentiart

```{r}
corpus_SentiArt <- corpus_all_entities_long %>%
  mutate(word = tolower(word)) %>%
  anti_join(stop_german, by = "word")

corpus_SentiArt <-  left_join(corpus_SentiArt, sentiart, by = "word")


```


#### proportional plot

```{r}
corpus_SentiArt2 %>%
  group_by(type) %>%
  mutate(row_n_type = n()) %>%
  group_by(type, emotion) %>%
  summarise(value_sum = sum(value_scaled)/row_n_type) %>%
  group_by(emotion) %>%
  distinct() %>%
  filter(!is.na(emotion)) %>%
  ggplot(aes(x = emotion, y = value_sum, fill = emotion)) +    
  geom_bar(stat = 'identity') +
  theme_sjplot2() +
  theme(legend.position = 'none', # get rid of legend
        axis.text.x = element_text(angle = 45, hjust = 1, size = fs/1.5)) + 
  scale_fill_simpsons() +
  facet_grid(. ~ type)
```


### fear

```{r fig.height=7, fig.width=10}
corpus_SentiArt %>% 
  ggplot(aes(type, fear_z, fill = type)) +
  geom_boxplot(na.rm = T) +
  theme_sjplot2() +
  scale_fill_simpsons() +
  # if unified nat_term and CH_rural
    ggpubr::stat_compare_means(method = "wilcox.test",
                             comparisons = list(c("CH_rural", "CH_urban")),
                             na.rm = T,
                             label = "p.signif")
```

#### summary

```{r}

Rmisc::summarySE(corpus_SentiArt,
                 measurevar = "fear_z",
          groupvars = c("type"),
          na.rm = TRUE,
          conf.interval = 0.95)

```

#### compare means

```{r}
compare_means(fear_z ~ type, data = corpus_SentiArt, method = "wilcox.test")

```

### disgust

```{r fig.height=7, fig.width=10}

corpus_SentiArt %>% 
  ggplot(aes(type, disg_z, fill = type)) +
  geom_boxplot() +
  theme_sjplot2() +
  scale_fill_simpsons()+
  # if unified nat_term and CH_rural
    ggpubr::stat_compare_means(method = "wilcox.test",
                             comparisons = list(c("CH_rural", "CH_urban")),
                             na.rm = T,
                             label = "p.signif")
```

#### summary

```{r}

Rmisc::summarySE(corpus_SentiArt, measurevar = "disg_z",
          groupvars = c("type"),
          na.rm = TRUE,
          conf.interval = 0.95)

```

#### compare means

```{r}
compare_means(disg_z ~ type, data = corpus_SentiArt, method = "wilcox.test")

```

### happyness

```{r fig.height=7, fig.width=10}

corpus_SentiArt %>% 
  ggplot(aes(type, hap_z, fill = type)) +
  geom_boxplot() +
  theme_sjplot2() +
  scale_fill_simpsons()+
  # if unified nat_term and CH_rural
    ggpubr::stat_compare_means(method = "wilcox.test",
                             comparisons = list(c("CH_rural", "CH_urban")),
                             na.rm = T,
                             label = "p.signif")

```

#### summary

```{r}

Rmisc::summarySE(corpus_SentiArt, measurevar = "hap_z",
          groupvars = c("type"),
          na.rm = TRUE,
          conf.interval = 0.95)

```

#### compare means

```{r}
compare_means(hap_z ~ type, data = corpus_SentiArt, method = "wilcox.test")

```

### sadness

```{r fig.height=7, fig.width=10}

corpus_SentiArt %>% 
  ggplot(aes(type, sad_z, fill = type)) +
  geom_boxplot() +
  theme_sjplot2() +
  scale_fill_simpsons()+
  # if unified nat_term and CH_rural
    ggpubr::stat_compare_means(method = "wilcox.test",
                             comparisons = list(c("CH_rural", "CH_urban")),
                             na.rm = T,
                             label = "p.signif")
```

#### summary

```{r}

Rmisc::summarySE(corpus_SentiArt, measurevar = "sad_z",
          groupvars = c("type"),
          na.rm = TRUE,
          conf.interval = 0.95)

```

#### compare means

```{r}
compare_means(sad_z ~ type, data = corpus_SentiArt, method = "wilcox.test")

```

### surprise

```{r fig.height=7, fig.width=10}

corpus_SentiArt %>% 
  ggplot(aes(type, surp_z, fill = type)) +
  geom_boxplot() +
  theme_sjplot2() +
  scale_fill_simpsons()+
  # if unified nat_term and CH_rural
    ggpubr::stat_compare_means(method = "wilcox.test",
                             comparisons = list(c("CH_rural", "CH_urban")),
                             na.rm = T,
                             label = "p.signif")

```

#### summary

```{r}

Rmisc::summarySE(corpus_SentiArt, measurevar = "surp_z",
          groupvars = c("type"),
          na.rm = TRUE,
          conf.interval = 0.95)

```

#### compare means

```{r}
compare_means(surp_z ~ type, data = corpus_SentiArt, method = "wilcox.test")

```

### anger

```{r fig.height=7, fig.width=10}

corpus_SentiArt %>% 
  ggplot(aes(type, ang_z, fill = type)) +
  geom_boxplot() +
  theme_sjplot2() +
  scale_fill_simpsons()+
  # if unified nat_term and CH_rural
    ggpubr::stat_compare_means(method = "wilcox.test",
                             comparisons = list(c("CH_rural", "CH_urban")),
                             na.rm = T,
                             label = "p.signif")

```

#### summary

```{r}

Rmisc::summarySE(corpus_SentiArt, measurevar = "ang_z",
          groupvars = c("type"),
          na.rm = TRUE,
          conf.interval = 0.95)

```

#### compare means

```{r}
compare_means(ang_z ~ type, data = corpus_SentiArt, method = "wilcox.test")

```


```{r}


corpus_SentiArt2 <- corpus_SentiArt %>%
  pivot_longer(11:17, names_to = "emotion", values_to = "value")

lowest_negative_value = min(corpus_SentiArt2$value, na.rm = T)

corpus_SentiArt2 <- corpus_SentiArt2 %>%
  mutate(value_scaled = value - lowest_negative_value)

corpus_SentiArt2 <- corpus_SentiArt2 %>%
  dplyr::group_by(type, author, title, doc_id, pattern, emotion) %>%
  summarise(value_scaled = mean(value_scaled, na.rm = T), freq = mean(freq, na.rm = T))
  
```

```{r}
summary(corpus_SentiArt2)
```



```{r}
corpus_SentiArt2  %>%
  # summarise(value = mean(value)) %>%
  ggplot(aes(x = emotion, y = value_scaled, fill = type)) +
  # ylim(-1,1) +
  # facet_wrap(~ type, scales = "free_y") +
  geom_boxplot(position = "dodge") +
  theme_sjplot2() +
  theme(legend.position = 'right', # get rid of legend
        axis.text.x = element_text(angle = 45, hjust = 1, size = fs/1.5)) + 
  scale_fill_simpsons() +
  # if unified nat_term and CH_rural
    ggpubr::stat_compare_means(method = "wilcox.test",
                             comparisons = list(c("CH_rural", "CH_urban")),
                             na.rm = T,
                             label = "p.signif")

```



#### lmer

```{r}
sentiart_lmer <- lmer(value_scaled ~ type +
                        (1|emotion) + 
                        (1|freq) +
                        (1|title),
     corpus_SentiArt2, REML = F)

tab_model(sentiart_lmer, show.se = T,
            show.ci = F,
            show.stat = T,
            emph.p = T,
            transform = NULL,
            string.pred = "Pred",
            string.stat = "z",
            string.se = "SE",
            show.icc = F) %>%
  return() %$% 
  knitr %>% 
  knitr::asis_output()
```

