---
title: "Test paper - corpus prep"
author: "Giulia Grisot"
date: "2020"
output:
  html_notebook: 
    number_sections: no
    theme: flatly
---

# Corpus preparation

```{r message=FALSE, warning=F}

library(tidyverse)
library(tidytext)
library(sjPlot)
library(ggsci)
# library(wesanderson)
library(wordcloud)
library(readxl)
library(plyr)

```

## method 1 Load txt files from a directory and prepare text corpus

```{r}
# 
# # read in texts (file name must be in the format: surname_section_year.txt)
# # for instructions about how to see:  https://data.library.virginia.edu/a-beginners-guide-to-text-analysis-with-quanteda/
# 
# heidi_1 <- readtext::readtext("spyri_heidilehr_1880.txt", encoding = "UTF-8")
# heidi_2 <- readtext::readtext("spyri_heidibrauchen_1881.txt", encoding = "UTF-8")
# 
# 
# heidi <- list(
#  heidi_1 = heidi_1$text,
#  heidi_2 = heidi_2$text
# ) %>%
#  ldply(rbind) %>%
#   mutate(book = .id) %>%
#   mutate(text = `1`) %>%
#   select(-1,-2)
# 
# heidi_sentences <- heidi %>%
#   unnest_tokens(sentence, text, token = "sentences", to_lower = F)
# 
# heidi_words <- heidi %>%
#   unnest_tokens(word, text, token = "words", to_lower = F)

```

## method 2 Load epub files from a directory and prepare text corpus
this preserves chapter data

```{r}

# read in texts (file name must be in the format: surname_section_year.txt)
# for instructions about how to see:  https://data.library.virginia.edu/a-beginners-guide-to-text-analysis-with-quanteda/

library(epubr)

heidi <- as.data.frame(epub("other_texts/spyri_heidi_1880_2.epub"))

heidi <- unnest(heidi, data)

heidi_txt <- heidi[11:35, ]



```

```{r}

heidi_sentences <- heidi_txt %>%
  unnest_tokens(sentence, text, token = "sentences", to_lower = F)

heidi_words <- heidi_txt %>%
  unnest_tokens(word, text, token = "words", to_lower = F)

```


```{r}

heidi_words <- heidi_words %>%
  mutate(type = if_else(nword < 10, "title", "chapter")) %>%
  mutate(ch_n = as.integer(factor(section, levels = unique(.$section)))) %>%
  mutate(book = if_else(ch_n < 16, "book1", "book2"))

heidi_words$book <- as.factor(heidi_words$book)

heidi_words <- heidi_words %>% filter(!(str_detect(word, "\\d"))) #remove rows containing numbers in the word column



heidi_sentences <- heidi_sentences %>%
  mutate(type = if_else(nword < 10, "title", "chapter")) %>%
  mutate(ch_n = as.integer(factor(section, levels = unique(.$section)))) %>%
  mutate(book = if_else(ch_n < 16, "book1", "book2"))

heidi_sentences$book <- as.factor(heidi_sentences$book)

heidi_sentences <- heidi_sentences %>% filter(!(str_detect(sentence, "\\d"))) #remove rows containing numbers in the word column

```

## Stop words

A next step would be to examine word frequencies.

- let's start by making a dataset of german stop words that will then be removed from the corpus

```{r}
stop_german <- tibble(word = stopwords::stopwords("de"))
stop_french <- tibble(word = stopwords::stopwords("fr"))
stop_ita <- tibble(word = stopwords::stopwords("it"))
```

# add sentence case stopwords

```{r}
stop_german2 <- stop_german
stop_german2$word <- str_to_sentence(stop_german2$word)
stop_german <- bind_rows(stop_german, stop_german2)
remove(stop_german2)
```

## Add word ID and Frequencies 

```{r}
heidi_sentences <- heidi_sentences %>%
  dplyr::mutate(sentence_id = row_number())

heidi_words <- heidi_words %>%
  dplyr::mutate(word_id = row_number())

```


```{r}
## Load txt files from a directory and prepare text corpus
# text_all <- text_all %>% filter(!(str_detect(word, "\\d"))) #remove rows containing numbers in the word column

```

# heidi names


```{r}
## indentify proper names
heidi_names <- c("heidi", "öhi", "clara", "peter", "klara", "großmutter", "großvater", "großmama", "sesemann", "rottenmeier", "sebastian", "alm-öhi")

heidi_names <- as.data.frame(heidi_names)
heidi_names2 <- heidi_names
heidi_names2$heidi_names <- str_to_sentence(heidi_names2$heidi_names)

heidi_names <- heidi_names %>%
  bind_rows(heidi_names2) %>%
  mutate(word = heidi_names) %>%
  select(word)

remove(heidi_names2)

```

# Sentiment Dictionaries

## SentiWS

let's alter the SentiWS dictionary to include all forms of the different tokens

```{r}

sentiWS <- pradadata::sentiws
sentiWS_long <- unnest_tokens(sentiWS, word2, inflections, to_lower = F)

# there are some empty rows in word2 column, which should be the same as word. let's fill the gaps.

sentiWS_long1 <- sentiWS_long %>%
  select(4,1,3) %>%
  mutate(word = word2) %>%
  select(-word2)

sentiWS_long2 <- sentiWS_long %>%
  select(2,1,3)

# sentiWS_long$word <- tolower(sentiWS_long$word2)

sentiWS_long <- bind_rows(sentiWS_long2, sentiWS_long1)

sentiWS_long <- sentiWS_long %>%
  dplyr::rename(SentiWS_neg_pos = neg_pos) %>%
  dplyr::rename(SentiWS_polarity = value)

remove(sentiWS, sentiWS_long1, sentiWS_long2)


```

## Glex

```{r}
glex <- pradadata::germanlex
glex <- glex %>%
  dplyr::rename(glex_neg_pos = qualifier) %>%
  dplyr::rename(glex_polarity = polarity_strength)

# there seem to be a few words that are not right in the dataset. let's take them out

glex <- filter(glex, word != "%%")

```

## SentiART

```{r}
sentiart <- read.csv("SA_resources/SentiArt.dat", dec = ",")

sentiart_long <- sentiart %>%
  select(-1) %>%
  gather(emotion, value, -word)

sentiart_long_top <- sentiart_long %>% 
  group_by(word) %>% 
  slice_max(value)

```

## Plutchnik

```{r, message=F}

plutchik <- read_csv("SA_resources/Plutchik_Emotionslexikon.csv")

plutchik <- plutchik %>%
  filter(!is.na(Wortart)) %>%
  filter(!is.na(word))

plutchik$word <- plutchik$`#Term`
plutchik$emotion <- plutchik$`Emotion 1`

plutchik$`#Term` <- NULL
plutchik$`Emotion 1` <- NULL

plutchik <- plutchik %>%
  filter(emotion != "??" & emotion != "??emotion??")

plutchik$emotion <- as.factor(plutchik$emotion)

```

## LANG

```{r, message=F}
LANG_processed <- read_table2("SA_resources/LANG_processed.csv")

```

## BAWL

```{r, message=F}
BAWL <- read_csv("SA_resources/BAWL-R.csv")

CapStr <- function(y) {
  c <- strsplit(y, " ")[[1]]
  paste(toupper(substring(c, 1,1)), substring(c, 2),
        sep="", collapse=" ")
}

for(i in 1:length(BAWL$WORD)){
  
  if(BAWL$WORD_CLASS[i] == "N")
    BAWL$WORD_LOWER[i] <- CapStr(BAWL$WORD_LOWER[i])
  
}

BAWL_emotions <- data.frame(word = BAWL$WORD_LOWER, valence = BAWL$EMO_MEAN, arousal = BAWL$AROUSAL_MEAN, imageability = BAWL$IMAGE_MEAN, stringsAsFactors = F)


```

## Klinger

```{r, warning=F, message=F}

ekel <- read_table("SA_resources/Klinger_emotion_lexicon/Ekel.txt", col_names = F) %>%
  mutate(emotion = "ekel", word = X1) %>%
  select(-X1)
freude <- read_csv("SA_resources/Klinger_emotion_lexicon/Freude.txt", col_names = F)%>%
  mutate(emotion = "freude", word = X1) %>%
  select(-X1)
furcht <- read_csv("SA_resources/Klinger_emotion_lexicon/Furcht.txt", col_names = F)%>%
  mutate(emotion = "furcht", word = X1) %>%
  select(-X1)
trauer <- read_csv("SA_resources/Klinger_emotion_lexicon/Trauer.txt", col_names = F)%>%
  mutate(emotion = "trauer", word = X1) %>%
  select(-X1)
ueberraschung <- read_csv("SA_resources/Klinger_emotion_lexicon/Ueberraschung.txt", col_names = F)%>%
  mutate(emotion = "ueberraschung", word = X1) %>%
  select(-X1)
verachtung <- read_csv("SA_resources/Klinger_emotion_lexicon/Verachtung.txt", col_names = F)%>%
  mutate(emotion = "verachtung", word = X1) %>%
  select(-X1)
wut <- read_csv("SA_resources/Klinger_emotion_lexicon/wut.txt", col_names = F)%>%
  mutate(emotion = "wut", word = X1) %>%
  select(-X1)

klinger <- bind_rows(ekel, freude, furcht, trauer, ueberraschung, verachtung, wut)

remove(ekel, freude, furcht, trauer, ueberraschung, verachtung, wut)
```




# Geolocations & NER


## geological/natural terms

german terms from openthesaurus, modified url for different categories (29, 5, 6)

https://www.openthesaurus.de/term/list?max=1705&offset=0&categoryId=6


```{r}
# geogr_terms <- geogr_terms <- read_excel("Geolocation and maps/geogr_terms.xlsx", 
#                                          sheet = "All_nodoub", col_types = c("text", 
#                                                                              "skip", "text"))
# geogr_terms <- read_excel("Geolocation and maps/geogr_terms.xlsx",
#                                          sheet = "Geologie")

nat_terms <- read_excel("Geolocation and map data/geogr_terms_new.xlsx", 
    sheet = "Selected")

nat_terms <- nat_terms %>%
   dplyr::filter(!is.na(word)) %>%
   dplyr::filter(!grepl("\\d", word))

nat_terms <- nat_terms %>%
   dplyr::filter(word != "Mann" &
                    word != "Q" &
                    word != "Frau" &
                    word != "Frauen" &
                    word != "Drei" &
                    word != "Tisch" &
                    word != "gezerrt" &
                    word != "David" &
                    word != "Rolle" &
                    word != "Joseph" &
                    word != "Alte" &
                    word != "Jungen" &
                    word != "Don" &
                    word != "Donna" &
                    word != "Maria" &
                    word != "Tal" &
                    word != "Erstes" &
                    word != "B" &
                    word != "Heinrich" &
                    word != "Garten" &
                    word != "Lee" &
                    word != "Mittel" &
                    word != "Art" &
                    word != "Wagen" &
                    word != "Speck" &
                    word != "Morgen" &
                    word != "Schönen" &
                    word != "Mitte" &
                    word != "Buch" &
                    word != "Plan" &
                    word != "Alter" &
                    word != "Luft" &
                    word != "Erste" &
                    word != "Enge" &
                    word != "Stock" &
                    word != "Gottes" &
                    word != "Vogel" &
                    word != "Schule" &
                    word != "Wasser" &
                    word != "Lohn" &
                    word != "Brot" &
                    word != "Nie" &
                    word != "Grauen" &
                    word != "Kleine" &
                    word != "Laufen" &
                    word != "Jakob" &
                    word != "Auge" &
                    word != "Jungen" &
                    word != "Spiegel" &
                    word != "Meyer" &
                    word != "Loch" &
                    word != "Innere" &
                    word != "Leid" &
                    word != "Teilen" &
                    word != "Mauer" &
                    word != "Mut" &
                    word != "Ei" &
                    word != "Arten" &
                    word != "Ring" &
                    word != "Aussicht" &
                    word != "Zug" &
                    word != "B" &
                    word != "Felix" &
                    word != "Inhalte" &
                    word != "Tante" &
                    word != "Margot" &
                    word != "Anna" &
                    word != "Dritte" &
                    word != "Ach" &
                    word != "Beim" &
                    word != "Rosa" &
                    word != "Jean" &
                    word != "Frohe" &
                    word != "U" &
                    word != "Schwarz" &
                    word != "Michael" &
                    word != "Peter" &
                    word != "Sebastian" &
                    word != "Hund" &
                    word != "Marc" &
                    word != "Signora" &
                    word != "Valentino" &
                    word != "Piano" &
                    word != "Zweites" &
                    word != "Viertes" &
                    word != "Nase" &
                    word != "Base" &
                    word != "Kuchen" &
                    word != "Satz" &
                    word != "Gips" &
                    word != "Roten" &
                    word != "Krone" &
                    word != "Rot" &
                    word != "Gelb" &
                    word != "Rad" &
                    word != "Prosa" &
                    word != "Lag" &
                    word != "Bestellung" &
                    word != "Vater" &
                    word != "Mein" &
                    word != "Bruder" &
                    word != "Zeit" &
                    word != "Numa" &
                    word != "West" &
                    word != "Ost" &
                    word != "Ab" &
                    word != "B" &
                    word != "Ach")


# natural_features_from_Text_Berg <- read_csv("natura features from Text+Berg.csv", 
#                                            col_types = cols(rank = col_skip(), `count T+B` = col_skip()))
# 
# T_B_list <- natura_features_from_Text_Berg$word

# geogr_terms <- geogr_terms %>%
#   unnest_tokens(word, geologie)  %>%
#   distinct() %>%
#   mutate(geo_term = "yes")


```




## swiss places

```{r}
library(readxl)
# swiss_places_source <- read_excel("CH/swiss_places.xlsx",  sheet = "Sheet1",
#                            col_types = c("skip", "text", "text", 
#                                          "text", "numeric", "numeric", "text", 
#                                          "text", "text", "text", "text", "numeric", 
#                                          "numeric", "numeric", "numeric", 
#                                          "numeric", "skip", "skip", "skip", 
#                                          "skip"))


swiss_places <- read_excel("CH/swiss_places.xlsx", 
    sheet = "Sheet1", col_types = c("skip", 
        "text", "text", "text", "numeric", 
        "numeric", "text", "text", "text", 
        "text", "text", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "skip", "skip", "skip", "skip"))

swiss_places <- swiss_places %>%
  anti_join(nat_terms, by = "word")

```


<!-- ```{r} -->

<!-- CH_country_regions <- swiss_places %>% -->
<!--   filter(type == "A") %>% -->
<!--   distinct() -->

<!-- CH_streams_lake <- swiss_places %>% -->
<!--   filter(type == "H")%>% -->
<!--   distinct() -->

<!-- CH_park_areas <- swiss_places %>% -->
<!--   filter(type == "L") %>% -->
<!--   distinct() -->

<!-- CH_city_village <- swiss_places %>% -->
<!--   filter(type == "P") %>% -->
<!--   distinct() -->

<!-- CH_roads <- swiss_places %>% -->
<!--   filter(type == "R") %>% -->
<!--   distinct() -->

<!-- CH_building_spots <- swiss_places %>% -->
<!--   filter(type == "S") %>% -->
<!--   distinct() -->

<!-- CH_mountain_hill <- swiss_places %>% -->
<!--   filter(type == "T") %>% -->
<!--   distinct() -->

<!-- CH_forests <- swiss_places %>% -->
<!--   filter(type == "V") %>% -->
<!--   distinct() -->

<!-- ``` -->



<!-- ```{r} -->
<!-- swiss_places <- swiss_places_source %>% -->
<!--   dplyr::select(name_1, name_2, name_3, type) -->


<!-- swiss_places1  <- swiss_places %>% -->
<!--   unnest_tokens(name, name_1, token = "words", to_lower = F) %>% -->
<!--   select(type, name) -->

<!-- swiss_places2  <- swiss_places %>% -->
<!--   unnest_tokens(name, name_2, token = "words", to_lower = F)  %>% -->
<!--   select(type, name) -->

<!-- swiss_places3  <- swiss_places %>% -->
<!--   unnest_tokens(name, name_3, token = "words", to_lower = F)  %>% -->
<!--   select(type, name) -->

<!-- swiss_places <- bind_rows(swiss_places1, swiss_places2, swiss_places3) -->

<!-- remove(swiss_places1, swiss_places2, swiss_places3) -->


<!-- # swiss_places <- swiss_places %>% -->
<!-- #   dplyr::filter(!grepl("\\(", name)) %>% -->
<!-- #   dplyr::filter(!grepl("\\)", name)) %>% -->
<!-- #   dplyr::filter(!grepl("\\d", name)) %>% -->
<!-- #   dplyr::filter(!grepl("/", name)) %>% -->
<!-- #   dplyr::filter(!grepl("&", name)) %>% -->
<!-- #   dplyr::filter(!grepl("\\[", name)) %>% -->
<!-- #   dplyr::filter(!grepl("\\]", name)) -->


<!-- swiss_places <- swiss_places %>% -->
<!--   filter(!is.na(name))  %>% -->
<!--   filter(name != "-") -->


<!-- # swiss_places <- swiss_places %>% -->
<!-- #   tidytext::unnest_tokens(name, name, token = "words", to_lower = F) -->

<!--  swiss_places <- swiss_places %>% -->
<!--    dplyr::filter(!is.na(name)) -->

<!--  swiss_places <- swiss_places %>% -->
<!--     dplyr::filter(!grepl("\\d", name)) -->

```{r}
swiss_places <- swiss_places %>%
   dplyr::filter(word != "Mann" &
                    word != "Q" &
                    word != "Frau" &
                    word != "Frauen" &
                    word != "Drei" &
                    word != "Tisch" &
                    word != "gezerrt" &
                    word != "David" &
                    word != "Rolle" &
                    word != "Joseph" &
                    word != "Alte" &
                    word != "Jungen" &
                    word != "Don" &
                    word != "Donna" &
                    word != "Maria" &
                    word != "Tal" &
                    word != "Erstes" &
                    word != "B" &
                    word != "Heinrich" &
                    word != "Garten" &
                    word != "Lee" &
                    word != "Mittel" &
                    word != "Art" &
                    word != "Wagen" &
                    word != "Speck" &
                    word != "Morgen" &
                    word != "Schönen" &
                    word != "Mitte" &
                    word != "Buch" &
                    word != "Plan" &
                    word != "Alter" &
                    word != "Luft" &
                    word != "Erste" &
                    word != "Enge" &
                    word != "Stock" &
                    word != "Gottes" &
                    word != "Vogel" &
                    word != "Schule" &
                    word != "Wasser" &
                    word != "Lohn" &
                    word != "Brot" &
                    word != "Nie" &
                    word != "Grauen" &
                    word != "Kleine" &
                    word != "Laufen" &
                    word != "Jakob" &
                    word != "Auge" &
                    word != "Jungen" &
                    word != "Spiegel" &
                    word != "Meyer" &
                    word != "Loch" &
                    word != "Innere" &
                    word != "Leid" &
                    word != "Teilen" &
                    word != "Mauer" &
                    word != "Mut" &
                    word != "Ei" &
                    word != "Arten" &
                    word != "Ring" &
                    word != "Aussicht" &
                    word != "Zug" &
                    word != "B" &
                    word != "Felix" &
                    word != "Inhalte" &
                    word != "Tante" &
                    word != "Margot" &
                    word != "Anna" &
                    word != "Dritte" &
                    word != "Ach" &
                    word != "Beim" &
                    word != "Rosa" &
                    word != "Jean" &
                    word != "Frohe" &
                    word != "U" &
                    word != "Schwarz" &
                    word != "Michael" &
                    word != "Peter" &
                    word != "Sebastian" &
                    word != "Hund" &
                    word != "Marc" &
                    word != "Signora" &
                    word != "Valentino" &
                    word != "Piano" &
                    word != "Zweites" &
                    word != "Viertes" &
                    word != "Nase" &
                    word != "Base" &
                    word != "Kuchen" &
                    word != "Satz" &
                    word != "Gips" &
                    word != "Roten" &
                    word != "Krone" &
                    word != "Rot" &
                    word != "Gelb" &
                    word != "Rad" &
                    word != "Prosa" &
                    word != "Lag" &
                    word != "Bestellung" &
                    word != "Vater" &
                    word != "Mein" &
                    word != "Bruder" &
                    word != "Zeit" &
                    word != "Numa" &
                    word != "West" &
                    word != "Ost" &
                    word != "Ab" &
                    word != "B" &
                    word != "Ach")

```


<!-- ````{r} -->

<!-- swiss_places$name <- tolower(swiss_places$name) -->


<!-- swiss_places <- swiss_places %>% dplyr::anti_join(stop_german, by = c("name" = "word")) -->
<!-- swiss_places <- swiss_places %>% dplyr::anti_join(stop_ita, by = c("name" = "word")) -->
<!-- swiss_places <- swiss_places %>% dplyr::anti_join(stop_french, by = c("name" = "word")) -->


<!-- swiss_places <- distinct(swiss_places) -->



<!-- swiss_places_wide <- swiss_places %>% -->
<!--   tidyr::pivot_wider(values_from = "type", names_from="type") -->

<!-- names(swiss_places_wide)[2:9] <- c("type1", "type2", "type3", "type4", "type5", "type6", "type7", "type8") -->

<!-- swiss_places_wide$name <- str_to_title(swiss_places_wide$name) -->
<!-- # swiss_places$geo_loc = "GPE" -->

<!-- swiss_places_wide <- swiss_places_wide %>% -->
<!--    filter(!str_detect(name, "\\.")) -->

<!-- swiss_places <- swiss_places %>% -->
<!--    filter(!str_detect(name, "\\.")) -->

<!-- swiss_places$name <- str_to_title(swiss_places$name) -->

<!-- # swiss_places_wide <- swiss_places_wide %>% dplyr::anti_join(removables) -->

<!-- swiss_places_list <- swiss_places_wide$name -->

<!-- jsonlite::write_json(swiss_places_list, "swiss_gpe.json") -->

<!-- ``` -->


# check entities

let's have a look if any items appear both in the rural lists and in the urban

```{r}

all_entities_wide <- nat_terms %>%
  mutate(type = label) %>%
  select(word, type) %>%
  bind_rows(swiss_places) %>%
  select(word, type) %>%
  pivot_wider(values_from = "type", names_from="type", values_fn = length)

all_entities_long <- all_entities_wide %>%
  pivot_longer(cols = 2:10) %>%
  filter(!is.na(value)) %>%
  mutate(type = name) %>%
  select(-value, -name)

all_entities_long$type[all_entities_long$type == "A"] <-  "country_region_state"
all_entities_long$type[all_entities_long$type == "P"] <-  "city_village"
all_entities_long$type[all_entities_long$type == "R"] <-  "roads"
all_entities_long$type[all_entities_long$type == "S"] <-  "spot_building"
all_entities_long$type[all_entities_long$type == "L"] <-  "park_area"
all_entities_long$type[all_entities_long$type == "T"] <-  "mountain"
all_entities_long$type[all_entities_long$type == "V"] <-  "forest"
all_entities_long$type[all_entities_long$type == "H"] <-  "stream_lake"

all_entities_long  <- all_entities_long %>%
  mutate(type2 = type)

all_entities_long$type2[all_entities_long$type2 == "country_region_state"] <-  "CH_urban"
all_entities_long$type2[all_entities_long$type2 == "city_village"] <-  "CH_urban"
all_entities_long$type2[all_entities_long$type2 == "roads"] <-  "CH_urban"
all_entities_long$type2[all_entities_long$type2 == "spot_building"] <-  NA
all_entities_long$type2[all_entities_long$type2 == "park_area"] <-  NA
all_entities_long$type2[all_entities_long$type2 == "mountain"] <-  "CH_rural"
all_entities_long$type2[all_entities_long$type2 == "forest"] <-  "CH_rural"
all_entities_long$type2[all_entities_long$type2 == "stream_lake"] <-  "CH_rural"


```


A = country region state
P = city village
R = roads

S = spot building farm
L = park areas

T = mountains
V = forests
H = streams lakes




# vector lists of Swiss places by type

```{r}
# CH_country_regions <- CH_country_regions$word
# 
# CH_streams_lake <- CH_streams_lake$word
# 
# CH_park_areas <- CH_park_areas$word
# 
# CH_city_village <- CH_city_village$word
# 
# CH_roads <- CH_roads$word
# 
# CH_building_spots <- CH_building_spots$word
# 
# CH_mountain_hill <- CH_mountain_hill$word
# 
# CH_forests <- CH_forests$word

CH_country_regions <- all_entities_wide %>%
  filter(is.na(P) & is.na(R) & is.na(V) & is.na(`T`) & is.na(H) & is.na(S) & is.na(L) & is.na(nat_term))
CH_country_regions_list <- CH_country_regions$word

CH_streams_lake <-  all_entities_wide %>%
  filter(is.na(P) & is.na(R) & is.na(V) & is.na(`T`) & is.na(A) & is.na(S) & is.na(L) & is.na(nat_term))
CH_streams_lake_list <- CH_streams_lake$word

CH_city_village <- all_entities_wide %>%
  filter(is.na(A) & is.na(R) & is.na(V) & is.na(`T`) & is.na(H) & is.na(S) & is.na(L) & is.na(nat_term))
CH_city_village_list <- CH_city_village$word

CH_roads <- all_entities_wide %>%
  filter(is.na(A) & is.na(P) & is.na(V) & is.na(`T`) & is.na(H) & is.na(S) & is.na(L) & is.na(nat_term))
CH_roads_list <- CH_roads$word

CH_mountain_hill <- all_entities_wide %>%
  filter(is.na(A) & is.na(P) & is.na(V) & is.na(R) & is.na(H) & is.na(S) & is.na(L) & is.na(nat_term))
CH_mountain_hill_list <- CH_mountain_hill$word

CH_forests <- all_entities_wide %>%
  filter(is.na(A) & is.na(P) & is.na(R) & is.na(`T`) & is.na(H) & is.na(S) & is.na(L) & is.na(nat_term))
CH_forests_list <- CH_forests$word

CH_park_areas <- all_entities_wide %>%
  filter(is.na(A) & is.na(P) & is.na(R) & is.na(`T`) & is.na(H) & is.na(S) & is.na(V) & is.na(nat_term))
CH_park_areas_list <- CH_park_areas$word

CH_building_spots <- all_entities_wide %>%
  filter(is.na(A) & is.na(P) & is.na(R) & is.na(`T`) & is.na(H) & is.na(V) & is.na(L) & is.na(nat_term))
CH_building_spots_list <- CH_building_spots$word

```



```{r}
# nat_terms <- all_entities_wide %>%
#   filter(is.na(A) & is.na(P) & is.na(R) & is.na(`T`) & is.na(H) & is.na(V) & is.na(L) & is.na(S))
nat_terms_list <- nat_terms$word

# nat_terms_list <- c(nat_terms_list,T_B_list)

# geo_all <- append(geo_all, swiss_places$name)
  
# jsonlite::write_json(geo_all, "geo_all.json")
```


# vector lists of Swiss places urban vs. rural


```{r}
# CH_urban <- swiss_places %>%
#   filter(type == "A" | type == "P" | type == "R" | type == "S") %>%
#    select("name") %>%
#    distinct()


# CH_rural <- swiss_places %>%
#   filter(type == "H" | type == "T" | type == "L" | type == "V" | type == "nat_term") %>%
#    select("name") %>%
#    distinct()



# 
# CH_urban <- swiss_places_selected %>%
#   filter(urban == "yes")
# 
# 
# CH_rural <- swiss_places_selected %>%
#   filter(rural == "yes")

CH_urban <- bind_rows(CH_country_regions, CH_roads, CH_city_village)

CH_rural <- bind_rows(CH_mountain_hill, CH_forests, CH_streams_lake)


CH_rural_list <- CH_rural$word

CH_urban_list <- CH_urban$word

```